### Importing libraries

```{r, message=F, warning=F}
library(tidyverse)
library(patchwork)
library(cheapr) #For e.g. scm
```

```{r}
start_idx <- 910000 #Walk
stop_idx <-  927000 #Walk
start_idx <- 6436351 #Cycle
stop_idx <- 6471301 #Cycle
start_idx <- 4172500 #Car
stop_idx <- 4208400 #Car
start_idx <- 5644150 #Run 
stop_idx <- 5695381 #Run
```

```{r}
start_idx <- 910801
stop_idx <- 925201
temp <- df_part_trim[start_idx:stop_idx,3] %>% scale()
N <- length(temp)
spec <- alt_fft(temp)
spec %>% plot(type = "h")

#Continue here 03-12 and 04-12, finally normalisation works correctly
#Test that indeed the proportions, energy within certain components, works as well now
```

Step 1: consider what the occurring frequencies are in the spectrum on a large scale. We use the "determine_hills" function which works on "alt_fft" spectrums. Following two inputs need to be considered carefully:
- Hill_thresh: Could for example be determined based on variance, or if proportion with ma_peak is higher or lower than proportion with mean values, etc. Should be dependent on the total length of the spectrum (e.g. of the mean value) though. Using constant times mean it will be harsh on shorter spectrums
- Hill_significance: when is a hill as a whole significant? Note that we already only include values in the hill for which ma is high enough, so not risk that the hill just grows very big. Not clear if it should have some dependence on length of the hill/spectrum as well. 

```{r}
hills <- determine_hills(5, spec, 0.0005, 0.05)
```

We can now determine the weighted mean value for both, and through this the middle index and thus the corresponding frequency.

```{r}
movement_frequencies <- c()

for(hill in hills){
  hill_values <- spec[hill]
  hill_centre <- (min(hill) - 1 + (sum(hill_values*(1:length(hill_values)))/sum(hill_values))) #Can round, but do not even have to I think
  hill_freq <- (N)/hill_centre #We divide by hill_centre and not hill_centre minus 1, as we already removed DC component in computing the alt_spec
  movement_frequencies <- append(movement_frequencies, hill_freq)
}
```

---

We now apply these findings to an example, to see how consistent this maximum frequency is in periodic data and noisy data.

```{r}
N <- 601 #Show consistent/stable under this parameter as well? Don't know to what extent it is
period_wdw <- (N-1)/2

ma_wdw_spec <- 5 #Show consistent/stable under this parameter
hill_thresh <- 3/period_wdw #Show consistent/stable under this parameter
hill_significance <- 0.05 #Show consistent/stable under this parameter
  
start_idx <- 910801 #Walk
stop_idx <- 925201 #Walk

start_idx <- 6406469 #Cycle
stop_idx <- 6420091 #Cycle

start_idx <- 3928501 #Car
stop_idx <-  3956401 #Car

start_idx <- 270000 #Stair_segment
stop_idx <- 290000 #Stair_segment

start_idx <- 305000 #Test brief walk
stop_idx <-  315000 #Test
  
data <- df_part_trim[start_idx:stop_idx,3]
data_scaled <- df_part_trim[start_idx:stop_idx,3] %>% scale()
#Scaling immediately could be problematic, although needed for ways hills are detected now

main_frequencies <- numeric(length(data_scaled) - 2*period_wdw)
second_frequencies <- numeric(length(data_scaled) - 2*period_wdw)
third_frequencies <- numeric(length(data_scaled) - 2*period_wdw)

for(j in (period_wdw + 1):(length(data_scaled) - period_wdw)){
  spec <- alt_fft(data_scaled[(j - period_wdw):(j + period_wdw)])
  hills <- determine_hills(ma_wdw_spec, spec, hill_thresh, hill_significance)
  
  frequencies <- get_hill_frequencies(spec, hills, N)

  main_frequencies[j - period_wdw] <- ifelse(is.null(frequencies[1]), 0, frequencies[1])
  #Need this weird if statement here, because apparently if frequencies has just one element,
  #then frequencies[2] and [3] are counted as NA and not as null
  if(is.null(frequencies[1])){
    second_frequencies[j - period_wdw] <- ifelse(is.null(frequencies[2]), 0, frequencies[2])
    third_frequencies[j - period_wdw] <- ifelse(is.null(frequencies[3]), 0, frequencies[3])
  }
  else{
    second_frequencies[j - period_wdw] <- ifelse(is.na(frequencies[2]), 0, frequencies[2])
    third_frequencies[j - period_wdw] <- ifelse(is.na(frequencies[3]), 0, frequencies[3])
  }
  #Still generates NA values that should be 0. I don't see where the NA values are coming from. I would think either frequencies[1] is null, or it contains some value.

}

plot(main_frequencies, type = "l")
plot(second_frequencies, type = "l")
plot(third_frequencies, type = "l")
```

Now that we know the main frequency, we can both zoom in more to see where the movement with that frequency starts/stops, and we can use it to see if we have a periodic movement at all. There's two approaches, either through some LCM just determine if one strong movement at every point, or first use the big scale to see where continuously some movement appears, and then either only looking at those on small scale, or even just trying to find stopping point and starting point of signal (but not advisable, as it will pick up pauses and we want to extract double-steps).

Our first approach will be from mainly the main_frequency, get out periods during which one movement dominates, and then seeing if there is a second_frequency and third_frequency consistent throughout that period as well. 

```{r}
ma_wdw_raw <- 5
ma_wdw_diff <- 25
thresh_change <- 1/100 #How to determine? Thought 1/N made sense, but due to ways hill are chosen it may shift a lot more unexpectedly 
#This can be seen (maybe) as a way to decide how certain we want to be that we do not classify different movements as the same, where the trade-off is missing out on movements. Other parameters can be described similarly.

data_ma <- ma(data_scaled, n = ma_wdw_raw)

#Define a data frame which only contains data for which we could compute the frequency values
central_df <- data.frame(idx = 1:(length(data_scaled) - 2*period_wdw), data_scaled = data_scaled[(period_wdw + 1):(length(data_scaled) - period_wdw)], data_ma = data_ma[(period_wdw + 1):(length(data_scaled) - period_wdw)], main_freq = main_frequencies, second_freq = second_frequencies, third_freq = third_frequencies)

central_df <- mutate(central_df, main_freq_diff = c(0, diff(main_frequencies)))
central_df <- mutate(central_df, second_freq_diff = c(0, diff(second_frequencies)))
central_df <- mutate(central_df, third_freq_diff = c(0, diff(third_frequencies)))

central_df <- mutate(central_df, main_freq_diff_ma = ma(abs(main_freq_diff), n = ma_wdw_diff))
#Instead of approach with main_freq_diff_ma above limit, we may want to extract periods in which variance is limited or sth like that

central_df <- mutate(central_df, consistent_values = ifelse(main_freq_diff_ma > thresh_change, 0, 1))

central_df <- mutate(central_df, movement_num = with(rle(ifelse(is.na(central_df$consistent_values), 0, central_df$consistent_values != 0)), inverse.rle(list(values = ifelse(values, cumsum(values), 0), lengths = lengths)) * (!is.na(central_df$consistent_values) & central_df$consistent_values != 0)))


peakness <- c(0, diff(sign(diff(data_ma))), 0)
is_peak <- ifelse(peakness == -2, 1, 0) 
central_df$peak <- is_peak[(1 + period_wdw):(length(is_peak) - period_wdw)]
```

```{r}
min_movement_length <- N+5 #We need at least N, because we drop period_wdw on both sides when analysing. This procedure can be relaxed later. We take N+5 for now such that this central part is not just one value which can happen to be weird for whatever reason.
thresh_zero_freq <- 0.1
thresh_var_freq <- 0.2
lcm_tol <- 0.7 #Should this depend on which frequency we detect? Having high values would lead to bigger variance than low values, so this would be harsher on movement where the second frequency is relatively high maybe

thresh_acf <- 0.3 #how high must the lead_freq correlation be for us to recognise it as a periodic movement/steps

step_collections <- list()
  
for(j in (1:max(central_df$movement_num))){
  indices <- which(central_df$movement_num == j)
  
  if(length(indices) >= min_movement_length){
    #Only if we are in a movement with consistent values (not too much change) that is big enough
    
    central_part_mvm <- central_df[(min(indices) + period_wdw):(max(indices) - period_wdw),]
    #We are interested in the middle of this movement. Can be broadened later.
    main_freq_mvm <- mean(central_part_mvm$main_freq)
    
    #Now check if we should also consider a second frequency
    if(sum(central_part_mvm$second_freq == 0)/length(central_part_mvm$second_freq) >= thresh_zero_freq){
      second_freq_mvm <- 0 #No second frequency if too many zeroes
    } else if(var(central_part_mvm$second_freq[central_part_mvm$second_freq != 0]) >= thresh_var_freq) {
      second_freq_mvm <- 0 #Too much variance, so no consistent second frequency
      #Maybe we should first get out a small fraction of most extreme values or sth here, so that if almost everywhere second_freq 
      #is 12, but at a few observations it is suddenly 35, the variance does not blow up
    } else{
      second_freq_mvm <- mean(central_part_mvm$second_freq)
    }
    
    #Now we compute the leading frequency. For now limited to at most two main frequencies, but same process should be done for possible third frequency maybe. For now it would be filtered out anyway because it is 0 so often
    
    if(second_freq_mvm == 0){
      lead_freq_mvm <- main_freq_mvm %>% round() #Rounding can be more refined?
    }
    else {
    lead_freq_mvm <- scm(c(main_freq_mvm, second_freq_mvm), tol = lcm_tol) %>% round() #Rounding can be more refined?
    }
    
    steps_in_mvm <- list()
    step_one <- c() #Initialising as empty so that we can compare with them
    step_two <- c() #Initialising as empty so that we can compare with them
    continuation <- FALSE
    
    zero_idx <- min(indices) - 1 #We count from this one
    
    k <- 1 #k is the index within the current movement we are at
    while(k <= length(indices)){
      #print(k)
      if(central_df$peak[zero_idx + k] == 1) { #Same as [indices][k] in this case
        #print("peak detected")
        
        #We first check if lead_freq (+/- 1 error) from our peak we have a new peak
        #We have to be careful! For our last few peaks, this might not be within indices
        
        if(central_df$peak[zero_idx + k + lead_freq_mvm] == 1){
          end <- zero_idx + k + lead_freq_mvm
        } else if(central_df$peak[zero_idx + k + lead_freq_mvm + 1] == 1){
          #Later choose between first checking +1 and first checking -1
          end <- zero_idx + k + lead_freq_mvm + 1
        } else if(central_df$peak[zero_idx + k - lead_freq_mvm - 1] == 1){
          end <- zero_idx + k + lead_freq_mvm - 1
        } else {
          end <- NA
        }
        
        if(!is.na(end)){
          if(central_df$peak[zero_idx + k - lead_freq_mvm] == 1) {
            start <- zero_idx + k - lead_freq_mvm
            } else if(central_df$peak[zero_idx + k - (lead_freq_mvm - 1)] == 1){
              start <- zero_idx + k - (lead_freq_mvm - 1)
            } else if(central_df$peak[zero_idx + k - (lead_freq_mvm + 1)] == 1){
              start <- zero_idx + k - (lead_freq_mvm + 1)
            } else {
              start <- NA
            }
        }
        
        if(!is.na(end) & !is.na(start)){
          #Check from start to end if correlation at the frequency of that step is very high (alternative: check if very high at the lead frequency of the whole movement, because that sort of should be the case as well, as we assume it is the same movement thus with the same frequencies!?)
          #If yes, we add these two steps and continue from the end index again
          
          lead_freq_part <- (end - start)/2
          if(lead_freq_part %% 1 != 0){
            if(lead_freq_mvm > lead_freq_part){
              lead_freq_part <- ceiling(lead_freq_part)
            } else{
              lead_freq_part <- floor(lead_freq_part)
            }
          } 
          
          #We have start, zero_idx + k and end
          acf_step <- acf(central_df$data_scaled[start:(end-1)], lag.max = lead_freq_part)
          
          if(acf_step[lead_freq_mvm]$acf > thresh_acf) {
            step_one <- central_df$data_scaled[start:(zero_idx + k - 1)]
            
            #We only need to add step_one, if it is not just a continuation from step_two,
            #so if we did not just add there. I think doing it like this is sufficient
            if(continuation == FALSE) {
              steps_in_mvm <- append(steps_in_mvm, list(step_one))
            }
            
            step_two <- central_df$data_scaled[(zero_idx + k):(end - 1)]
            
            steps_in_mvm <- append(steps_in_mvm, list(step_two)) 
            #print(length(steps_in_mvm)) #Bug test
          
            
            continuation <- TRUE #Meaning we have just added steps and continue from the last step
            
            
          } #If not, nothing happens. It is just not periodic enough and we do not recognise them as steps. Having two peaks was by chance
          else{
            continuation <- FALSE
          }
          
          #If no, we can also safely skip this part of the movement
          k <- end - zero_idx #We continue with "end", which is a peak, being our new peak
          
          
        }else{
          k <- k + 1 #If the current peak was not successful, we keep looking but do not skip a period
          continuation <- FALSE
        }
      } else{
        k <- k + 1 #If we were not at a peak, we just look at the next one 
        continuation <- FALSE
      }
    }
    
    step_collections <- append(step_collections, list(number = j, summary = c(lead_freq_mvm, main_freq_mvm, second_freq_mvm), examples = steps_in_mvm))
  }
}
```

Testing // show in meeting
- Fix bugs for other periods
- Fix scaling
- Make sure it can allow for more than two steps in row. Seems to work in theory, but not picked up as often as you would think?
- Rounds up the lead_freq from main_freq and second_freq

```{r}
step_collections[[82]]
step_collections[[2]]
plot(step_collections[[3]][[1]], type = "l")
plot(step_collections[[3]][[2]], type = "l")
plot(step_collections[[3]][[3]], type = "l")
plot(step_collections[[3]][[4]], type = "l")
plot(step_collections[[3]][[5]], type = "l")
plot(step_collections[[3]][[6]], type = "l")
plot(step_collections[[3]][[7]], type = "l")
plot(step_collections[[3]][[8]], type = "l")
plot(step_collections[[3]][[9]], type = "l")
plot(step_collections[[3]][[10]], type = "l")
plot(step_collections[[84]][[11]], type = "l")
plot(step_collections[[84]][[12]], type = "l")
plot(step_collections[[84]][[13]], type = "l")
plot(step_collections[[84]][[14]], type = "l")
plot(step_collections[[84]][[15]], type = "l")
plot(step_collections[[84]][[16]], type = "l")
plot(step_collections[[84]][[17]], type = "l")
plot(step_collections[[84]][[18]], type = "l")
plot(step_collections[[84]][[19]], type = "l")
plot(step_collections[[84]][[20]], type = "l")
plot(step_collections[[84]][[21]], type = "l")
plot(step_collections[[84]][[22]], type = "l")
plot(step_collections[[84]][[23]], type = "l")
plot(step_collections[[84]][[24]], type = "l")
plot(step_collections[[84]][[25]], type = "l")

```

--- 
Below alternative that just establishes the lead frequency, and will deal with those outside of the loop. 

```{r}
min_movement_length <- N+5 #We need at least N, because we drop period_wdw on both sides when analysing. This procedure can be relaxed later. We take N+5 for now such that this central part is not just one value which can happen to be weird for whatever reason.
thresh_zero_freq <- 0.1
thresh_var_freq <- 0.2
lcm_tol <- 0.7 #Should this depend on which frequency we detect? Having high values would lead to bigger variance than low values, so this would be harsher on movement where the second frequency is relatively high maybe

central_df <- mutate(central_df, lead_freq = 0)

for(j in (1:max(central_df$movement_num))){
  lead_freq_mvm <- 0 
  indices <- which(central_df$movement_num == j)
  
  if(length(indices) >= min_movement_length){
    
    central_part_mvm <- central_df[(min(indices) + period_wdw):(max(indices) - period_wdw),]
    main_freq_mvm <- mean(central_part_mvm$main_freq)
    
    #Now check if we should also consider a second frequency
    if(sum(central_part_mvm$second_freq == 0)/length(central_part_mvm$second_freq) >= thresh_zero_freq){
      second_freq_mvm <- 0 #No second frequency if too many zeroes
    } else if(var(central_part_mvm$second_freq[central_part_mvm$second_freq != 0]) >= thresh_var_freq) {
      second_freq_mvm <- 0 #Too much variance, so no consistent second frequency
      #Maybe we should first get out a small fraction of most extreme values or sth here, so that if almost everywhere second_freq 
      #is 12, but at a few observations it is suddenly 35, the variance does not blow up
    } else{
      second_freq_mvm <- mean(central_part_mvm$second_freq)
    }
    
    #Now we compute the leading frequency. For now limited to at most two main frequencies, but same process should be done for possible third frequency maybe. For now it would be filtered out anyway because it is 0 so often
    
    if(second_freq_mvm == 0){
      lead_freq_mvm <- main_freq_mvm %>% round() #Rounding can be more refined?
    }
    else {
    lead_freq_mvm <- scm(c(main_freq_mvm, second_freq_mvm), tol = lcm_tol) %>% round() #Rounding can be more refined?
    }
  }
  central_df$lead_freq[indices] <- lead_freq_mvm #Maybe more needs to be saved than just the lead_freq. After all, we want to make sure we can see the differences between steps in different movements
}
```

