### Importing libraries

```{r, message=F, warning=F}
library(tidyverse)
library(patchwork)
```

Sample periodic signal
```{r}
temp <- sin(1:1000)+sin((1:1000)/4)+sin((1:1000)/10)+sin(2*(1:1000))
plot(Mod(fft(temp)), type = "h")
```

Sample shifted periodic signal
```{r}
temp <- c(sin(1:10), c(0,0,0), sin(1:24), c(0,0), sin(1:18), c(0,0,0,0,0,0), sin(1:5), c(0,0), sin(1:41), c(0,0), sin(1:61), c(0,0,0,0)) 
plot(Mod(fft(temp)), type = "h")
```

Situation 1: interruption/noise, but still underlying signal that continues. So noise is multiple of 20
Situation 2: no underlying signal, noise has different length

```{r}
noise_length <- 0
temp <- c(sin((1:100)*pi/10), rep(0, noise_length), sin((1:100)*pi/10)) 
plot(temp, type = "l")
Mod(fft(temp)) %>% order(decreasing = T)
Mod(fft(temp)) %>% max()
Mod(fft(temp)) %>% plot(type = "h")
```

Situation 1: picks up underlying signal. Highest fourier component will be around 100 no matter length noise, which would correspond to length of function where this is the periodicity being 200 (?)
Situation 2: no longer true. The peak is still for a period of 20, but it is lower, especially if the noise length is close to half a period. However, if the noise length is long, the peak gets close to 100 again. 

Now situation 3: noise can have different lengths, but the signal now picks up at a different moment
```{r}
noise_length <- 0
temp <- c(sin((1:100)*pi/10), rep(0, noise_length), sin(pi + (1:100)*pi/10)) 
plot(temp, type = "l")
Mod(fft(temp)) %>% order(decreasing = T)
Mod(fft(temp)) %>% max()
Mod(fft(temp)) %>% plot(type = "h")
```

Test: how does the Fourier transform deal with signals that have clear periodicity, but do not look like a sinusoid

```{r}
temp <- rep(c(1,2,2,4,6,6,7,3,4,6, 3, 4, 3, 2, -1, -2, 1, 2, -2, 0), 20)
plot(temp, type = "h")
Mod(fft(temp)) %>% order(decreasing = T)
Mod(fft(temp)) %>% max()
Mod(fft(temp)) %>% plot(type = "h")
```

### The reverse Fourier transform

```{r}
temp <- df[(car_idx_1[1]+1000):(car_idx_1[1]+1199),11] 
temp <- df[(cycle_idx_1[1]+1000):(cycle_idx_1[1]+1199),11] 
plot(temp, type = "l")

temp_spectrum <- fft(temp)
plot(Mod(temp_spectrum)[2:length(temp_spectrum)], type = "h")
temp_spectrum
inverse_fourier(temp_spectrum, 1:length(temp)) %>% plot(type = "l")

sum(Mod(temp_spectrum))

temp_approx <- inverse_fourier_approx(temp_spectrum, 1:length(temp), 7)
temp_approx
temp_approx %>% plot(type = "l")
```

### Trying and understanding what spectrum looks like with smoothed data

```{r}
temp <- df[(walk_idx_1[1]+1000):(walk_idx_1[1]+1199),3] 
temp <- ma(temp, n = 1)
plot(temp, type = "l")
temp <- temp[!is.na(temp)]

temp_spectrum <- fft(temp)
plot(Mod(temp_spectrum)[2:length(temp_spectrum)], type = "h")

temp_approx <- inverse_fourier_approx(temp_spectrum, 1:length(temp), 3)
plot(temp, type = "l")
lines(temp_approx, type = "l", col = "red")


temp <- df[(car_idx_1[1]+1000):(car_idx_1[1]+1199),3] 
temp <- ma(temp, n = 1)
plot(temp, type = "l")
temp <- temp[!is.na(temp)]

temp_spectrum <- fft(temp)
plot(Mod(temp_spectrum)[2:length(temp_spectrum)], type = "h")

temp_approx <- inverse_fourier_approx(temp_spectrum, 1:length(temp), 9)
plot(temp, type = "l")
lines(temp_approx, type = "l", col = "red")
```

### Trying and understanding what spectrum looks like with tricky data

```{r}
noise_length <- 8
temp <- c(sin((1:100)*pi/10), rep(0, noise_length), sin((1:100)*pi/10), rep(0, noise_length), sin((1:100)*pi/10), rep(0, noise_length), sin((1:100)*pi/10), rep(0, noise_length), sin((1:100)*pi/10)) 
plot(temp, type = 'l')

temp_spectrum<- fft(temp)
order(Mod(temp_spectrum), decreasing = T)
temp_spectrum %>% Mod() %>% plot(type = 'h') 

temp_approx <- inverse_fourier_approx(temp_spectrum, 1:length(temp), 3)
plot(temp, type = "l")
lines(temp_approx, type = "l", col = "red")
```