```{r, message=F, warning=F}
#Data analysis
library(tidyverse)
library(latex2exp)
library(patchwork)
library(scales)
library(RColorBrewer)

#Working with the activity class and data files
library(lubridate)
library(read.gt3x)
library(PhysicalActivity)

#Solving equations
library(nleqslv)
library(pracma)
library(latex2exp)

#Reshaping / data manipulation
library(reshape2)
library(data.table)

##gganimate/creating animations
library(gganimate)
library(glue)
library(shiny)
library(av)
library(magick)
```

## Using the application
The approach to use the frameview application on Windows, for a video of at most 55 minutes and 33 seconds (99999 frames), is as follows: 
1. Make a folder called frames (if you want to preserve the current infrastructure. This folder should be present with an example as well). Assign a name of your choice, say, "ExampleName", to the variable folder_name. Create a folder with this name with the code below and by and add your video to this newly c reated folder and give it the same name as the folder (in this case ExampleName). You may want to change the scale parameter depending on the device with which the video is taken and if it is vertical or horizontal
2. Add a folder called "video" within the folder ExampleName, or create it using the given code. Put all video frames inside this folder at 30fps running the ffmpeg command within system. You may want to add 
3. Run the code that creates the necessary folders from which the data will be read. This is done automatically based on the number of files in the video folder, meaning it has to be run after step 2.
4. Find the precise starting time of the video, e.g. the observation that matches the first frame in the video. Easiest to do this is by working with part of the video and raw data to see when it matches best. A semi-automated way to do this is given below. 
5. Determine all parameters for the image-generation: what steps do you want to extract, and how do you want to display it alongside the video frames. 
6. Run all appropriate functions as indicated below and load the server.

Possible errors:
- _video file format: e.g. .MTS. Change such that user has to specify these things ..._
- _... to be added. My manual seems to have been overwritten at some point, so I very quicklky made a substitute. I cannot find the old version within GitHub_ 

## Determining the starting time
1. Make approximation (but way to do so is gone, please contact me if you experience issues)
2. Select functions for raw frames, so that you can compare raw values to video footage
3. See how many you are off, input this, compute what starting time you should select as below

##Everything summary to quickly run

```{r}
shinyApp(ui = shiny_walkW1New[[1]], server = shiny_walkW1New[[2]])

shinyApp(ui = shiny_raw_walk1[[1]], server = shiny_raw_walk1[[2]])
shinyApp(ui = shiny_walkW1[[1]], server = shiny_walkW1[[2]])
shinyApp(ui = shiny_home1[[1]], server = shiny_home1[[2]])
shinyApp(ui = shiny_tread2[[1]], server = shiny_tread2[[2]])
```

## Example of the approach, applied to walkW1New

```{r}
#Step 1 + 2
df <- Walk1
folder_name <- "walkW1New"
dir.create(file.path("frames", folder_name), recursive = TRUE, showWarnings = FALSE)
dir.create(file.path("frames", folder_name, "video"), recursive = TRUE, showWarnings = FALSE)
cmd <- paste0("ffmpeg -ss 00:00:00 -t 3334 -i frames/", folder_name, "/", folder_name, ".MTS -q:v 3 -vf \"fps=30,scale=600:340\" frames/", folder_name, "/video/frame_%05d.jpg")
system(cmd)

#Step 3
vid_frames <- length(list.files(paste0("frames/", folder_name, "/video"), pattern = "\\.jpg"))
no_of_hundreds <- 1 + vid_frames %/% 100
for(j in 0:(no_of_hundreds-1)){
  dir.create(file.path("frames", folder_name, paste0("Sideways", j)), recursive = TRUE, showWarnings = FALSE)
  dir.create(file.path("frames", folder_name, paste0("Forward", j)), recursive = TRUE, showWarnings = FALSE)
  dir.create(file.path("frames", folder_name, paste0("Vertical", j)), recursive = TRUE, showWarnings = FALSE)
  }

#Step 4 (but determined with semi-automatic approach)
start_time <- as.POSIXct("2025-01-20 10:31:19.372")

#Step 5
#Display parameters
fw_bottom <- -Inf
fw_top <- Inf
vert_bottom <- -Inf
vert_top <- Inf
side_bottom <- -Inf
side_top <- Inf
fig_width <- 800
fig_height <- 320
fix_y <- F

#Step partition parameters
wdw_size <- 120
ma_data <- 5 #Maybe split up into two parameters, one for peak/valley and one for analysis
ma_energy <- 5 #Changed from 9. Better?
kernel_func <- ma_gauss 
std_dev <- 1
upright_thresh <- 0.75
abs_acc_thresh <- 0.1 
thresh_abs <- 0
thresh_rel <- 0.25 
min_step_period <- 5
max_step_period <- 40
period_len <- 5 
period_len_double <- 5
period_thresh <- 0.14
double_step_thresh <- 0.21
thresh_direction <- 0.3


#Step 6
dir.create(file.path("frames", folder_name, "Averages"), recursive = TRUE, showWarnings = FALSE)
dir.create(file.path("frames", folder_name, "Forward"), recursive = TRUE, showWarnings = FALSE)
dir.create(file.path("frames", folder_name, "Vertical"), recursive = TRUE, showWarnings = FALSE)
dir.create(file.path("frames", folder_name, "Sideways"), recursive = TRUE, showWarnings = FALSE)

data_walkW1New <- generate_data(folder_name,
                width, 
                start_time, 
                df,
                wdw_size,
                ma_data,
                ma_energy,
                kernel_func,
                std_dev,
                upright_thresh,
                abs_acc_thresh,
                thresh_abs,
                thresh_rel,
                min_step_period,
                max_step_period,
                period_len,
                period_len_double,
                period_thresh,
                double_step_thresh,
                thresh_direction)

steps_info_walkW1New <- df_all_from_mvm_alt_nofilter(data_walkW1New, 200, min_square_difference_vert)

generate_images_avg(steps_info_walkW1New, 0.8, folder_name)
  
generate_images(folder_name,
                         width, 
                         start_time, 
                         fw_bottom,
                         fw_top,
                         vert_bottom,
                         vert_top,
                         side_bottom,
                         side_top,
                         fig_width,
                         fig_height,
                         fix_y,
                         data_walkW1New)

streamvid <- "video"
stream1 <- "Forward"
stream2 <- "Vertical"
stream3 <- "Sideways"

shiny_walkW1New <- generate_server(vid_frames,
                         folder_name,
                         streamvid,
                         stream1,
                         stream2,
                         stream3)

shinyApp(ui = shiny_walkW1New[[1]], server = shiny_walkW1New[[2]])
```

## Example of finding a precise starting time, applied to walkW1New

```{r}
#step 1
raw_df <- Walk1
raw_folder_name <- "walkW1New"
dir.create(file.path("frames", raw_folder_name, "video_raw"), recursive = TRUE, showWarnings = FALSE)

start_vid_raw <- "00:00:10"
length_vid_raw <- "10"
cmd <- paste0(
  "ffmpeg -i frames/", raw_folder_name, "/", raw_folder_name, ".MTS ",
  " -ss ", start_vid_raw, 
  " -t ", length_vid_raw, 
  " -q:v 3 -vf \"fps=30,scale=600:340\" frames/", 
  raw_folder_name, "/video_raw/frame_%05d.jpg"
)
system(cmd)

#Step 2
estimated_start_time_raw <- as.POSIXct("2025-01-20 10:31:29.372")
#The estimated start time of the part of the video you use to calibrate

#Step 3
fw_bottom <- -Inf
fw_top <- Inf
vert_bottom <- -Inf
vert_top <- Inf
side_bottom <- -Inf
side_top <- Inf
fig_width <- 800
fig_height <- 320
fix_y <- F

#Step 4
dir.create(file.path("frames", raw_folder_name, "X"), recursive = TRUE, showWarnings = FALSE)
dir.create(file.path("frames", raw_folder_name, "Y"), recursive = TRUE, showWarnings = FALSE)
dir.create(file.path("frames", raw_folder_name, "Z"), recursive = TRUE, showWarnings = FALSE)

generate_raw_images(raw_folder_name,
                    width,
                    estimated_start_time_raw,
                    raw_df,
                    fix_y,
                    X_bottom,
                    X_top,
                    Y_bottom,
                    Y_top,
                    Z_bottom,
                    Z_top)

raw_streamvid <- "video_raw"
raw_stream1 <- "X"
raw_stream2 <- "Y"
raw_stream3 <- "Z"

raw_vid_frames <- length(list.files(paste0("frames/", folder_name, "/video_raw"), pattern = "\\.jpg"))

shiny_walkW1New_raw <- generate_server(raw_vid_frames,
                         raw_folder_name,
                         raw_streamvid,
                         raw_stream1,
                         raw_stream2,
                         raw_stream3)

shinyApp(ui = shiny_walkW1New_raw[[1]], server = shiny_walkW1New_raw[[2]])
```

```{r}
frames_difference <- 0
#How many frames the figures on the left are ahead of the video on the right
#If the figures on the left are behind, input a negative number

seconds <- as.numeric(as.POSIXct(start_vid_raw, format="%H:%M:%S")) - 
           as.numeric(as.POSIXct("00:00:00", format="%H:%M:%S"))

estimated_start_time_raw_new <- as.POSIXct(as.numeric(estimated_start_time_raw) - frames_difference/30)
#Can decide to run again with this new estimation of the start of the raw frames

estimated_start_time <- as.POSIXct(as.numeric(estimated_start_time_raw_new) - seconds)
```

## Example of finding an estimated starting time, applied to walkW1New

```{r}
raw_df <- Walk1
temp <- filter(Walk1, time > as.POSIXct("2025-01-20 10:35:28.000"), time <  as.POSIXct("2025-01-20 10:35:40.800"))
plot(temp$Y, type = 'l')
```


# END EXAMPLE / TUTORIAL
# BELOW IS OLD / APPLIED

## Everything for walkW1

```{r}
raw_df <- Walk1
start_time <- as.POSIXct("2025-01-20 10:31:19.372")
test <- raw_df %>% filter(time > start_time & time < start_time + 20)
plot(test$X, type = 'l')

start_time <- as.POSIXct("2025-04-08 15:18:16.50")
folder_name <- "walkW1"
cmd <- paste0("ffmpeg -ss 00:00:00 -t 70 -i frames/", folder_name, "/", folder_name, ".MTS -q:v 3 -vf \"fps=30,scale=600:340\" frames/", folder_name, "/raw/frame_%05d.jpg")
system(cmd)

width <- 15
fix_y <- F
X_bottom <- -5
X_top <- 5
Z_bottom <- -5
Z_top <- 5
Y_bottom <- -5
Y_top <- 5

generate_raw_images(folder_name,
                    width,
                    start_time,
                    raw_df,
                    fix_y,
                    X_bottom,
                    X_top,
                    Y_bottom,
                    Y_top,
                    Z_bottom,
                    Z_top)

streamvid <- "raw"
stream1 <- "X"
stream2 <- "Y"
stream3 <- "Z"

vid_frames <- length(list.files(paste0("frames/", folder_name, "/raw"), pattern = "\\.jpg"))

shiny_raw_walk1 <- generate_server(vid_frames,
                         folder_name,
                         streamvid,
                         stream1,
                         stream2,
                         stream3)

shinyApp(ui = shiny_raw_walk1[[1]], server = shiny_raw_walk1[[2]])
```

```{r}
cmd <- paste0("ffmpeg -ss 00:00:00 -t 500 -i frames/", folder_name, "/", folder_name, ".MTS -q:v 3 -vf \"fps=30,scale=600:340\" frames/", folder_name, "/video/frame_%05d.jpg")
system(cmd)

vid_frames <- length(list.files(paste0("frames/", folder_name, "/video"), pattern = "\\.jpg"))
start_time <- as.POSIXct("2025-01-20 10:31:19.372")

#Image generation parameters
fw_bottom <- -2.5
fw_top <- 2.5
vert_bottom <- -2.7
vert_top <- 2.2
side_bottom <- -1.5
side_top <- 1.5
fig_width <- 800
fig_height <- 320
fix_y <- T

#Step partition parameters
wdw_size <- 120
ma_data <- 5
ma_energy <- 9
kernel_func <- ma_gauss 
std_dev <- 1
upright_thresh <- 0.75
abs_acc_thresh <- 0.1 
thresh_abs <- 0.005 
thresh_rel <- 0.27 
min_step_period <- 5
max_step_period <- 40
period_len <- 5 
period_len_double <- 5 #This is what I changed! Used to be 1, but can be higher sensibly
period_thresh <- 0.14
double_step_thresh <- 0.21
thresh_direction <- 0.3

data_walkW1 <- generate_data(folder_name,
                width, 
                start_time, 
                raw_df,
                wdw_size,
                ma_data,
                ma_energy,
                kernel_func,
                std_dev,
                upright_thresh,
                abs_acc_thresh,
                thresh_abs,
                thresh_rel,
                min_step_period,
                max_step_period,
                period_len,
                period_len_double,
                period_thresh,
                double_step_thresh,
                thresh_direction)

steps_info_walkW1 <- df_all_from_mvm_alt_nofilter(data_walkW1, 200, min_square_difference_vert)

generate_images_avg(steps_info_walkW1, 0.8, folder_name)
  
generate_images(folder_name,
                         width, 
                         start_time, 
                         fw_bottom,
                         fw_top,
                         vert_bottom,
                         vert_top,
                         side_bottom,
                         side_top,
                         fig_width,
                         fig_height,
                         fix_y,
                         data_walkW1)

streamvid <- "video"
stream1 <- "Forward"
stream2 <- "Vertical"
stream3 <- "Sideways"

streamvid <- "raw"
stream1 <- "X"
stream2 <- "Y"
stream3 <- "Z"

shiny_walkW1 <- generate_server(vid_frames,
                         folder_name,
                         streamvid,
                         stream1,
                         stream2,
                         stream3)

shinyApp(ui = shiny_walkW1[[1]], server = shiny_walkW1[[2]])
```


##Everything for home1

Getting an idea of where the ending of the video roughly is

```{r}
raw_df <- N_video
start_time <- as.POSIXct("2025-04-08 15:18:26.500")
test <- raw_df %>% filter(time > start_time & time < start_time + 20)
plot(test$X, type = 'l')

start_time <- as.POSIXct("2025-04-08 15:18:16.500")
folder_name <- "home1"
cmd <- paste0("ffmpeg -ss 00:04:30 -t 300 -i frames/", folder_name, "/", folder_name, ".mp4 -q:v 3 -vf \"fps=30,scale=280:500\" frames/", folder_name, "/raw/frame_%05d.jpg")
system(cmd)

width <- 15
fix_y <- F
X_bottom <- -5
X_top <- 5
Z_bottom <- -5
Z_top <- 5
Y_bottom <- -5
Y_top <- 5

generate_raw_images(folder_name,
                    width,
                    start_time,
                    raw_df,
                    fix_y,
                    X_bottom,
                    X_top,
                    Y_bottom,
                    Y_top,
                    Z_bottom,
                    Z_top)

streamvid <- "raw"
stream1 <- "X"
stream2 <- "Y"
stream3 <- "Z"

vid_frames <- length(list.files(paste0("frames/", folder_name, "/raw"), pattern = "\\.jpg"))

shiny_raw_home1 <- generate_server(vid_frames,
                         folder_name,
                         streamvid,
                         stream1,
                         stream2,
                         stream3)

shinyApp(ui = shiny_raw_home1[[1]], server = shiny_raw_home1[[2]])
```

###Body!

Once the starting time has been established we can generate the images of oriented acceleration including steps and host the application.

```{r}
cmd <- paste0("ffmpeg -ss 00:00:00 -t 300 -i frames/", folder_name, "/", folder_name, ".mp4 -q:v 3 -vf \"fps=30,scale=280:500\" frames/", folder_name, "/video/frame_%05d.jpg")
system(cmd)

vid_frames <- length(list.files(paste0("frames/", folder_name, "/video"), pattern = "\\.jpg"))
start_time <- as.POSIXct("2025-04-08 15:13:53.972")

#Image generation parameters
fw_bottom <- -2.3
fw_top <- 2.3
vert_bottom <- -2.5
vert_top <- 2
side_bottom <- -1.3
side_top <- 1.3
fig_width <- 800
fig_height <- 320
fix_y <- T

#Step partition parameters
wdw_size <- 150
ma_data <- 5
ma_energy <- 9
kernel_func <- ma_gauss 
std_dev <- 1
upright_thresh <- 0.75
abs_acc_thresh <- 0.1 
thresh_abs <- 0.005 
thresh_rel <- 0.33 
min_step_period <- 5
max_step_period <- 40
period_len <- 4 
period_len_double <- 2 #This is what I changed! Used to be 1, but can be higher sensibly
period_thresh <- 0.18
double_step_thresh <- 0.27
thresh_direction <- 0.3

data_home1 <- generate_data(folder_name,
                width, 
                start_time, 
                raw_df,
                wdw_size,
                ma_data,
                ma_energy,
                kernel_func,
                std_dev,
                upright_thresh,
                abs_acc_thresh,
                thresh_abs,
                thresh_rel,
                min_step_period,
                max_step_period,
                period_len,
                period_len_double,
                period_thresh,
                double_step_thresh,
                thresh_direction)

steps_info_home1 <- df_all_from_mvm_alt_nofilter(data_home1, 200, min_square_difference_vert)

generate_images_avg(steps_info_home1, 0.8, folder_name)
  
generate_images(folder_name,
                         width, 
                         start_time, 
                         fw_bottom,
                         fw_top,
                         vert_bottom,
                         vert_top,
                         side_bottom,
                         side_top,
                         fig_width,
                         fig_height,
                         fix_y,
                         data)

streamvid <- "video"
stream1 <- "Forward"
stream2 <- "Vertical"
stream3 <- "Sideways"

streamvid <- "raw"
stream1 <- "X"
stream2 <- "Y"
stream3 <- "Z"

shiny_home1 <- generate_server(vid_frames,
                         folder_name,
                         streamvid,
                         stream1,
                         stream2,
                         stream3)

shinyApp(ui = shiny_home1[[1]], server = shiny_home1[[2]])
```





##Everything for tread2

Getting an idea of where the ending of the video roughly is

```{r}
start_time <- as.POSIXct("2025-04-08 11:14:39.800")
test <- raw_df %>% filter(time > start_time & time < start_time + 20)
plot(test$X, type = 'l')
```

We first have to generate a raw version of the application of the end of the video. This also helps in establishing a starting time.

```{r}
cmd <- paste0("ffmpeg -ss 00:00:00 -t 500 -i frames/", folder_name, "/", folder_name, ".mp4 -q:v 3 -vf \"fps=30,scale=500:280,transpose=2\" frames/", folder_name, "/raw/frame_%05d.jpg")
system(cmd)
start_time <- as.POSIXct("2025-04-08 11:14:23.335")
folder_name <- "tread2"

width <- 15
raw_df <- N_video
fix_y <- F
X_bottom <- -Inf
X_top <- Inf
Z_bottom <- -Inf
Z_top <- Inf
Y_bottom <- -Inf
Y_top <- Inf

generate_raw_images(folder_name,
                    width,
                    start_time,
                    raw_df,
                    fix_y,
                    X_bottom,
                    X_top,
                    Y_bottom,
                    Y_top,
                    Z_bottom,
                    Z_top)
```

#Body!

Once the starting time has been established we can generate the images of oriented acceleration including steps and host the application.

```{r}
#Start_time and associated frames
folder_name <- "tread2"
vid_frames <- length(list.files(paste0("frames/", folder_name, "/video"), pattern = "\\.jpg"))

cmd <- paste0("ffmpeg -ss 00:02:48 -t 30 -i frames/", folder_name, "/", folder_name, ".mp4 -q:v 3 -vf \"fps=30,scale=500:280,transpose=2\" frames/", folder_name, "/video/frame_%05d.jpg")
system(cmd)
start_time <- as.POSIXct("2025-04-08 11:09:23.800")

cmd <- paste0("ffmpeg -ss 00:00:00 -t 500 -i frames/", folder_name, "/", folder_name, ".mp4 -q:v 3 -vf \"fps=30,scale=500:280,transpose=2\" frames/", folder_name, "/video/frame_%05d.jpg")
system(cmd)
start_time <- as.POSIXct("2025-04-08 11:08:33.335")

#Dataframe selection and cleaning parameters
width <- 15
raw_df <- N_video

#Image generation parameters
fw_bottom <- -3
fw_top <- 3
vert_bottom <- -3
vert_top <- 2.5
side_bottom <- -1.6
side_top <- 1.6
fig_width <- 800
fig_height <- 320
fix_y <- T

#Step partition parameters
wdw_size <- 150
ma_data <- 5
ma_energy <- 9
kernel_func <- ma_gauss 
std_dev <- 1
upright_thresh <- 0.75
abs_acc_thresh <- 0.1 
thresh_abs <- 0.005 
thresh_rel <- 0.33 
min_step_period <- 5
max_step_period <- 40
period_len <- 5 
period_len_double <- 1
period_thresh <- 0.18
double_step_thresh <- 0.27
thresh_direction <- 0.3

data <- generate_data(folder_name,
                width, 
                start_time, 
                raw_df,
                wdw_size,
                ma_data,
                ma_energy,
                kernel_func,
                std_dev,
                upright_thresh,
                abs_acc_thresh,
                thresh_abs,
                thresh_rel,
                min_step_period,
                max_step_period,
                period_len,
                period_len_double,
                period_thresh,
                double_step_thresh,
                thresh_direction)

steps_info_tread2 <- df_all_from_mvm_alt_nofilter(data, 200, min_square_difference_vert)

generate_images_avg(steps_info_tread2, 0.2, folder_name)
  
generate_images(folder_name,
                         width, 
                         start_time, 
                         fw_bottom,
                         fw_top,
                         vert_bottom,
                         vert_top,
                         side_bottom,
                         side_top,
                         fig_width,
                         fig_height,
                         fix_y,
                         data)

streamvid <- "video"
stream1 <- "Forward"
stream2 <- "Vertical"
stream3 <- "Sideways"

streamvid <- "raw"
stream1 <- "X"
stream2 <- "Y"
stream3 <- "Z"

shiny_tread2 <- generate_server(vid_frames,
                         folder_name,
                         streamvid,
                         stream1,
                         stream2,
                         stream3)

shinyApp(ui = shiny_tread2[[1]], server = shiny_tread2[[2]])
```
