### Importing libraries
We first important the libraries we need.

```{r, message=F, warning=F}
#Data analysis
library(tidyverse)
library(latex2exp)
library(patchwork)
library(scales)
library(RColorBrewer)

#Working with the activity class and data files
library(lubridate)
library(read.gt3x)
library(PhysicalActivity)

#Solving equations
library(nleqslv)
library(pracma)
library(latex2exp)

#Reshaping / data manipulation
library(reshape2)
library(data.table)

##gganimate/creating animations
library(gganimate)
library(glue)
library(shiny)
library(av)
library(magick)
```

We first attempt it for very general data. Not just for our steps. In essence, we simply try to display one vector and slowly show more of it.

```{r}
temp <- A20_off[900000:900100,]
width <- 15   #Display 11 values at the same time
half_width <- (width - 1)/2
frame_tot <- nrow(temp) + 1 - width

frame_list <- c()
for(j in 1:frame_tot){
  frame_list <- append(frame_list, rep(j, width))
}

idx_list <- c()
for(j in 1:frame_tot){
  idx_list <- append(idx_list, temp$time[j:(j + width - 1)])
}

val_list <- c()
for(j in 1:frame_tot){
  val_list <- append(val_list, temp$Y[ j:(j + width - 1)])
}

colour_list <- c()
for(j in 1:frame_tot){
  colour_list <- append(colour_list, c(rep(0, half_width), 1, rep(0, half_width)))
}

new <- data.frame(frame = frame_list, idx = idx_list, value = val_list, colour = colour_list)

p <- ggplot(new, aes(x = idx, y = value)) +
  geom_line() +
  geom_point(aes(color = factor(colour), size = factor(colour))) +
  scale_colour_manual(values = c("0" = "black", "1" = "red")) +
  scale_size_manual(values = c("0" = 5, "1" = 15)) +
  transition_states(frame, transition_length = 0, state_length = 1) +
  view_follow(fixed_y = T)

anim_save("temp.mp4", animation = p, fps = 1, width = 2000, height = 800, nframes = frame_tot)

# Plot
# p <- ggplot(new, aes(x = idx, y = value, color = factor(colour))) +
#   geom_line(linewidth = 1.5) +
#   scale_color_manual(values = c("0" = "black", "1" = "red")) +
#   theme_minimal() +
#   labs(title = 'Test: {closest_state}', 
#        x = "Time", 
#        y = "Value") +
#   transition_states(frame, transition_length = 0, state_length = 1) +
#   ease_aes("linear") +
#   ylim(0, 5) +
#   theme_minimal() +
#   theme(
#     text = element_text(size = 14),            
#     axis.title = element_text(size = 14),      
#     axis.text = element_text(size = 14),       
#     legend.text = element_text(size = 14),     
#     legend.title = element_text(size = 14)     
#   ) +
#   guides(color = "none", alpha = "none")
```

What if we instead had to make such an animation from the list data which has individual sequences and steps? This also means between steps there can be gaps of nothing. 

```{r}
all <- list(A20_list[[1]][[2]], A20_list[[1]][[3]], A20_list[[1]][[4]])
temp <- data.frame()
mvm_num <- 0
for(j in all){
  mvm_num <- mvm_num + 1
  mvm_df <- j$data %>% mutate(mvm = mvm_num, overarch = j$overarch)
  temp <- rbind(temp, mvm_df)
}
temp <- temp %>% select(time, acc_fw, acc_vert, acc_side, in_step_bw, in_step_fw, mvm)
temp$time <- as.numeric(temp$time)
last_mvm <- max(temp$mvm)
if(last_mvm > 1){
 for(j in 1:(last_mvm - 1)){
   insert_after <- max(which(temp$mvm == j))
   time_before <- temp$time[insert_after]
   time_after <- temp$time[insert_after + 1]
   row_number <- round((time_after - time_before)*30) - 1
   for(k in 1:row_number){
     temp <- temp %>% add_row(time = time_before + (1/30)*k, acc_fw = 0, acc_vert = 0, acc_side = 0, in_step_bw = 0, in_step_fw = 0, mvm = 0, .after = insert_after - 1 + k)
   }
 } 
}
```

We can now make a video using this new dataframe

```{r}
width <- 15 
half_width <- (width - 1)/2
frame_tot <- nrow(temp) + 1 - width

frame_list <- c()
for(j in 1:frame_tot){
  frame_list <- append(frame_list, rep(j, width))
}

idx_list <- c()
for(j in 1:frame_tot){
  idx_list <- append(idx_list, temp$time[j:(j + width - 1)])
}

val_list <- c()
for(j in 1:frame_tot){
  val_list <- append(val_list, temp$acc_vert[ j:(j + width - 1)])
}

colour_function <- function(df, idx){
  if((df$in_step_bw[idx] == 0) & (df$in_step_fw[idx] == 0)){
    return(2)
  }
  else if((df$in_step_bw[idx] %% 2 == 1) | (df$in_step_fw[idx] %% 2 == 1)){
    return(3)
  }
  else{
    return(4)
  }
}

colour_function_test <- function(df, idx){
  if((df$mvm[idx] == 0)){
    return(2)
  }
  else if((df$mvm[idx] %% 2 == 1)){
    return(3)
  }
  else{
    return(4)
  }
}

# colour_list <- c()
# for(j in 1:frame_tot){
#   colour_list <- append(colour_list, c(rep(0, half_width), 1, rep(0, half_width)))
# }

alt_colour_list <- c()
for(j in 1:frame_tot){
  for(k in 1:half_width){
    alt_colour_list <- append(alt_colour_list, colour_function(temp, j - 1 + k))
  }
  alt_colour_list <- append(alt_colour_list, 1)
  for(k in 1:half_width){
    alt_colour_list <- append(alt_colour_list, colour_function(temp, j + half_width + k))
  }
}

#new <- data.frame(frame = frame_list, idx = idx_list, value = val_list, colour = colour_list)
new <- data.frame(frame = frame_list, idx = idx_list, value = val_list, colour = alt_colour_list)

p <- ggplot(new, aes(x = idx, y = value)) +
  geom_line() +
  geom_point(aes(color = factor(colour), size = factor(colour))) +
  scale_colour_manual(values = c("0" = "red", "1" = "black", "2" = "#984EA3", "3" = "#009E73", "4" = "#E69F00")) +
  scale_size_manual(values = c("0" = 5, "1" = 15, "2" = 5, "3" = 5, "4" = 5)) +
  transition_states(frame, transition_length = 0, state_length = 1) +
  view_follow(fixed_y = T)

anim_save("temp_new.mp4", animation = p, fps = 1, width = 2000, height = 800, nframes = frame_tot)
```

```{r}
animate(p, renderer = file_renderer(dir = "frames", prefix = "frame_", overwrite = TRUE), fps = 1, width = 800, height = 320, nframes = frame_tot)

ui <- fluidPage(
  titlePanel("Frame Viewer"),
  # Move slider and buttons above images
  sliderInput("frame", "Frame:", min = 1, max = frame_tot, value = 1, step = 1),
  fluidRow(
    column(10,
           actionButton("prev", "Previous"),
           actionButton("next", "Next"),
           actionButton("play_pause", "Play"),
           numericInput("delay", "Delay (s):", value = 1/30, min = 0, step = 1/90, width = "100px")
    )
  ),
  # Show both images side by side
  fluidRow(
    column(4, imageOutput("frame_img", width = "10%", height = "10px")),
    column(4, imageOutput("video_img", width = "10%", height = "10px"))
  )
)

server <- function(input, output, session) {
  frame_dir <- "frames"
  frame_video_dir <- "frames_video"
  
  frame_files <- list.files(frame_dir, pattern = "\\.jpg$", full.names = TRUE)
  frame_files <- sort(frame_files)
  
  video_files <- list.files(frame_video_dir, pattern = "\\.jpg$", full.names = TRUE)
  video_files <- sort(video_files)

  observe({
    updateSliderInput(session, "frame", max = length(frame_files))
  })

  observeEvent(input$`next`, {
    new_val <- min(input$frame + 1, length(frame_files))
    updateSliderInput(session, "frame", value = new_val)
  })

  observeEvent(input$prev, {
    new_val <- max(input$frame - 1, 1)
    updateSliderInput(session, "frame", value = new_val)
  })

  output$frame_img <- renderImage({
    list(src = frame_files[input$frame], contentType = 'image/jpg')
  }, deleteFile = FALSE)


  output$video_img <- renderImage({
    list(src = video_files[input$frame], contentType = 'image/jpg')
  }, deleteFile = FALSE)
  
  playing <- reactiveVal(FALSE)

  observeEvent(input$play_pause, {
    playing(!playing())
    updateActionButton(session, "play_pause", label = if (playing()) "Pause" else "Play")
    })
  # Timer to auto-advance frames
  observe({
    if (playing()) {
      new_val <- if (input$frame < frame_tot) input$frame + 1 else 1
      updateSliderInput(session, "frame", value = new_val)
      Sys.sleep(input$delay)
      }
    })
}

shinyApp(ui = ui, server = server)
```

We now test this for walking data in combination with 

```{r}
system("ffmpeg -i test_walk_MP4.mp4 -q:v 3 -vf \"fps=30,scale = 500:400\" frames_video/frame_%05d.jpg")
width <- 15

#Now just need the corresponding frames of , so exact right start and end time and then analyse it
#Firstly we guess the time
vid_frames <- length(list.files("frames_videos", pattern = "\\.jpg")) #frames_videos should still depend on the precise folder we are asking from. Should be variable in a function.
start_time <- as.POSIXct("2025-01-20 10:31:19.630")
end_time <- start_time - (1/30) + vid_frames/30 + (width - 1)*(1/30) 

#Has actually one fewer observvation than you would maybe want that gets added later. Look into this still
temp_df <- filter(df_walk_1, time >= start_time & time <= end_time) 
```

```{r}
wdw_size <- 150
ma_data <- 5
ma_energy <- 9
kernel_func <- ma_gauss 
std_dev <- 1
upright_thresh <- 0.75
abs_acc_thresh <- 0.1 #Can be both peak and valley. ``Sufficient acceleration''
#Do not want footsteps to be from peak to valley or from valley to peak though!!!
thresh_abs <- 0.005 
thresh_rel <- 0.33 
min_step_period <- 5
max_step_period <- 40
period_len <- 5 
period_len_double <- 1
period_thresh <- 0.18
double_step_thresh <- 0.27
thresh_direction <- 0.3

unordered_alt_walk_1 <- fast_extraction_algorithm(df_walk_1, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, abs_acc_thresh, thresh_abs, thresh_rel, min_step_period, max_step_period, period_len, period_len_double, period_thresh, double_step_thresh, thresh_direction, sigma = std_dev)

unordered_seq <- unordered_alt_walk_1

ordered_seq <- unordered_seq[order(sapply(unordered_seq, function(x) x$data$time[1]))]
```

```{r}
temp <- data.frame()
mvm_num <- 0
for(j in ordered_seq){
  mvm_num <- mvm_num + 1
  mvm_df <- j$data %>% mutate(mvm = mvm_num, overarch = j$overarch)
  temp <- rbind(temp, mvm_df)
}
temp <- temp %>% select(time, acc_fw, acc_vert, acc_side, in_step_bw, in_step_fw, mvm)
temp$time <- as.numeric(temp$time)
last_mvm <- max(temp$mvm)

#We now add blank space between the movements, if necessary
if(last_mvm > 1){
 for(j in 1:(last_mvm - 1)){
   insert_after <- max(which(temp$mvm == j))
   time_before <- temp$time[insert_after]
   time_after <- temp$time[insert_after + 1]
   row_number <- round((time_after - time_before)*30) - 1
   for(k in 1:row_number){
     temp <- temp %>% add_row(time = time_before + (1/30)*k, acc_fw = 0, acc_vert = 0, acc_side = 0, in_step_bw = 0, in_step_fw = 0, mvm = 0, .after = insert_after - 1 + k)
   }
 } 
}

#We now add blank space before the first and after the last movement to match video length
insert_before <- 1
time_before <- as.numeric(start_time) - 1/30 #The first we add is the first immediately after start_time
time_after <- temp$time[1]
row_number <- round((time_after - time_before)*30) - 1
row_number <- round((time_after - time_before)*30) - 1
   for(k in 1:row_number){
     temp <- temp %>% add_row(time = time_after - (1/30)*k, acc_fw = 0, acc_vert = 0, acc_side = 0, in_step_bw = 0, in_step_fw = 0, mvm = 0, .before = insert_before)
   }

#We now add a blank space after the last movement to match video length
insert_after <- nrow(temp)
time_before <- temp$time[nrow(temp)] 
time_after <- as.numeric(end_time) + 1/30
row_number <- round((time_after - time_before)*30) - 1
   for(k in 1:row_number){
     temp <- temp %>% add_row(time = time_before + (1/30)*k, acc_fw = 0, acc_vert = 0, acc_side = 0, in_step_bw = 0, in_step_fw = 0, mvm = 0, .after = insert_after - 1 + k)
   }

#Testing for correct times
# nrow(temp)
# for(j in 1:11978){
#   if(temp$time[j + 1] - temp$time[j] > 0.034){
#     print("Big gap")
#     print(j)
#   }
#   if(temp$time[j+1] - temp$time[j] < 0.033){
#     print("Small gap")
#     print(j)
#   }
#   if(temp$time[j+1] - temp$time[j] > 0.033 & temp$time[j + 1] - temp$time[j] < 0.034){
#     #print("correct")
#   }
# }

width <- 15 
half_width <- (width - 1)/2
frame_tot <- nrow(temp) + 1 - width

frame_list <- c()
for(j in 1:frame_tot){
  frame_list <- append(frame_list, rep(j, width))
}

idx_list <- c()
for(j in 1:frame_tot){
  idx_list <- append(idx_list, temp$time[j:(j + width - 1)])
}

val_list <- c()
for(j in 1:frame_tot){
  val_list <- append(val_list, temp$acc_vert[ j:(j + width - 1)])
}

colour_function <- function(df, idx){
  if((df$in_step_bw[idx] == 0) & (df$in_step_fw[idx] == 0)){
    return(2)
  }
  else if((df$in_step_bw[idx] %% 2 == 1) | (df$in_step_fw[idx] %% 2 == 1)){
    return(3)
  }
  else{
    return(4)
  }
}

alt_colour_list <- c()
for(j in 1:frame_tot){
  for(k in 1:half_width){
    alt_colour_list <- append(alt_colour_list, colour_function(temp, j - 1 + k))
  }
  alt_colour_list <- append(alt_colour_list, 1)
  for(k in 1:half_width){
    alt_colour_list <- append(alt_colour_list, colour_function(temp, j + half_width + k))
  }
}

new <- data.frame(frame = frame_list, idx = idx_list, value = val_list, colour = alt_colour_list)
(max(new$frame) == vid_frames) #Has to be true
(nrow(new)/width == vid_frames) #Has to be true as well
```

```{r}
p <- ggplot(new, aes(x = idx, y = value)) +
  geom_line() +
  geom_point(aes(color = factor(colour), size = factor(colour))) +
  scale_colour_manual(values = c("0" = "red", "1" = "black", "2" = "#984EA3", "3" = "#009E73", "4" = "#E69F00")) +
  scale_size_manual(values = c("0" = 5, "1" = 15, "2" = 5, "3" = 5, "4" = 5)) +
  transition_states(frame, transition_length = 0, state_length = 1) +
  view_follow() +
  ylim(-2.2, 1.6) #Fixes y as well, but more appropriately. Can remove this so that it changes which y values it considers
  #or view_follow(fixed_y = T)

animate(p, renderer = file_renderer(dir = "frames", prefix = "frame_", overwrite = TRUE), fps = 1, width = 80, height = 32, nframes = frame_tot)

ui <- fluidPage(
  titlePanel("Frame Viewer"),
  # Move slider and buttons above images
  sliderInput("frame", "Frame:", min = 1, max = frame_tot, value = 1, step = 1),
  fluidRow(
    column(10,
           actionButton("prev", "Previous"),
           actionButton("next", "Next"),
           actionButton("play_pause", "Play"),
           numericInput("delay", "Delay (s):", value = 1/30, min = 0, step = 1/90, width = "100px")
    )
  ),
  # Show both images side by side
  fluidRow(
    column(7, imageOutput("frame_img", width = "10%", height = "10px")),
    column(5, imageOutput("video_img", width = "10%", height = "10px"))
  )
)

server <- function(input, output, session) {
  frame_dir <- "frames"
  frame_video_dir <- "frames_video"
  
  frame_files <- list.files(frame_dir, pattern = "\\.png$", full.names = TRUE)
  frame_files <- sort(frame_files)
  
  video_files <- list.files(frame_video_dir, pattern = "\\.jpg$", full.names = TRUE)
  video_files <- sort(video_files)

  observe({
    updateSliderInput(session, "frame", max = length(frame_files))
  })

  observeEvent(input$`next`, {
    new_val <- min(input$frame + 1, length(frame_files))
    updateSliderInput(session, "frame", value = new_val)
  })

  observeEvent(input$prev, {
    new_val <- max(input$frame - 1, 1)
    updateSliderInput(session, "frame", value = new_val)
  })

  output$frame_img <- renderImage({
    list(src = frame_files[input$frame], contentType = 'image/png')
  }, deleteFile = FALSE)


  output$video_img <- renderImage({
    list(src = video_files[input$frame], contentType = 'image/jpg')
  }, deleteFile = FALSE)
  
  playing <- reactiveVal(FALSE)

  observeEvent(input$play_pause, {
    playing(!playing())
    updateActionButton(session, "play_pause", label = if (playing()) "Pause" else "Play")
    })
  # Timer to auto-advance frames
  observe({
    if (playing()) {
      new_val <- if (input$frame < frame_tot) input$frame + 1 else 1
      updateSliderInput(session, "frame", value = new_val)
      Sys.sleep(input$delay)
      }
    })
}

shinyApp(ui = ui, server = server)
```

### Below is the actual pipelin

```{r}
#system("ffmpeg -i test_walk_MP4.mp4 -q:v 3 -vf \"fps=30,scale = 500:400\" frames_video/frame_%05d.jpg")
#system("ffmpeg -t 60 -i test_thuis.mp4 -q:v 3 -vf \"fps=30,scale = 300:400\" test_thuis_vid/frame_%05d.jpg")
system("ffmpeg -ss 00:00:40 -t 30 -i tread2.mp4 -q:v 3 -vf \"fps=30,scale=470:260,transpose=2\" tread2_vid/frame_%05d.jpg")
```

```{r}
width <- 15
folder_name_vid_frames <- "tread2_vid"
vid_frames <- length(list.files(folder_name_vid_frames, pattern = "\\.jpg"))

start_time <- as.POSIXct("2025-04-08 15:13:53.000")
end_time <- start_time - (1/30) + vid_frames/30 + (width - 1)*(1/30) 

#test_df <- filter(N_video, time >= start_time & time <= end_time) 

#test <- filter(N_video, time > start_time & time < start_time + 40)
#plot(test$Z, type = 'l')

#plot(test_df$X, type = 'l')
```

```{r}
start_time <- as.POSIXct("2025-04-08 11:09:23.500")
tp <- filter(raw_df, time > start_time) %>% pull(Z)
plot(tp[1:200], type = 'l')
```

```{r}
start_time <- as.POSIXct("2025-04-08 11:09:23.800")
width <- 15
folder_name_vid_frames <- "tread2_vid"
vid_frames <- length(list.files(folder_name_vid_frames, pattern = "\\.jpg"))
raw_df <- N_video

vid_name <- "tread2.mp4"
folder_name_frames <- "tread2_frames"

fw_bottom <- -2.5
fw_top <- 2.5
vert_bottom <- -2.8
vert_top <- 2.2
side_bottom <- -1.5
side_top <- 1.5

fig_width <- 800
fig_height <- 320
fix_y <- T

wdw_size <- 150
ma_data <- 5
ma_energy <- 9
kernel_func <- ma_gauss 
std_dev <- 1
upright_thresh <- 0.75
abs_acc_thresh <- 0.1 #Can be both peak and valley. ``Sufficient acceleration''
#Do not want footsteps to be from peak to valley or from valley to peak though!!!
thresh_abs <- 0.005 
thresh_rel <- 0.33 
min_step_period <- 5
max_step_period <- 40
period_len <- 5 
period_len_double <- 1
period_thresh <- 0.18
double_step_thresh <- 0.27
thresh_direction <- 0.3

data <- generate_data(
                folder_name_vid_frames,
                width, 
                start_time, 
                raw_df,
                wdw_size,
                ma_data,
                ma_energy,
                kernel_func,
                std_dev,
                upright_thresh,
                abs_acc_thresh,
                thresh_abs,
                thresh_rel,
                min_step_period,
                max_step_period,
                period_len,
                period_len_double,
                period_thresh,
                double_step_thresh,
                thresh_direction)

shiny <- generate_server(vid_name,
                         folder_name_vid_frames,
                         folder_name_frames,
                         width, 
                         start_time, 
                         fw_bottom,
                         fw_top,
                         vert_bottom,
                         vert_top,
                         side_bottom,
                         side_top,
                         fig_width,
                         fig_height,
                         fix_y,
                         data)
```

```{r}
shinyApp(ui = shiny[[1]], server = shiny[[2]])

shinyApp(ui = ui, server = server)
```

#We now attempt the treadmil video, including finding out the starting time etc.

```{r}
system("ffmpeg -i tread2.mp4 -q:v 3 -vf \"fps=30,scale = 500:400,transpose=1\" tread2_vid/frame_%05d.jpg")
system("ffmpeg -sseof -20 -i tread2.mp4 -q:v 3 -vf \"fps=30,scale=500:400,transpose=2\" tread2_vid/frame_%05d.jpg")
system("ffmpeg -ss 00:02:48 -t 20 -i tread2.mp4 -q:v 3 -vf \"fps=30,scale=500:280,transpose=2\" tread2_vid/frame_%05d.jpg")

start_time <- as.POSIXct("2025-04-08 11:13:55.000")
width <- 15
folder_name_vid_frames <- "tread2_vid"
vid_frames <- length(list.files(folder_name_vid_frames, pattern = "\\.jpg"))
end_time <- start_time - (1/30) + vid_frames/30 + (width - 1)*(1/30) 
raw_df <- N_video %>% filter(time > start_time & time < end_time)

folder_name_vid_frames <- "tread2_vid"
folder_name_frames <- "tread2_frames"
width <- 15
ylim_bottom <- -0.9
ylim_top <- 0.7
fig_width <- 800
fig_height <- 320
fix_y <- T
data <- raw_df

shiny_raw <- generate_raw_server(
                         folder_name_vid_frames,
                         folder_name_frames,
                         width, 
                         ylim_bottom,
                         ylim_top,
                         fig_width,
                         fig_height,
                         fix_y,
                         data)
```

