```{r, message=F, warning=F}
#Data analysis
library(tidyverse)
library(latex2exp)
library(patchwork)
library(scales)
library(RColorBrewer)

#Working with the activity class and data files
library(lubridate)
library(read.gt3x)
library(PhysicalActivity)

#Solving equations
library(nleqslv)
library(pracma)
library(latex2exp)

#Reshaping / data manipulation
library(reshape2)
library(data.table)
library(zeallot)

##gganimate/creating animations
library(gganimate)
library(glue)
library(shiny)
library(av)
library(magick)
```

# Examples all with spasm data, later generalise for more data after getting approach

## General: data

```{r}
#Purely analysis of what is on video (5 seconds on both sides):
start_time <- as.POSIXct("2025-04-15 11:34:52.099999")
end_time <- as.POSIXct("2025-04-15 11:35:51.099999")
df_spas_vid <- filter(Misc3, time > start_time & time < end_time)

start_time <- as.POSIXct("2025-01-20 15:37:28.266666")
end_time <- as.POSIXct("2025-01-20 15:44:28.266666")
df_alt_vid <- filter(Walk2, time > start_time & time < end_time)

df <- df_alt_vid

wdw_size <- 120
ma_data <- 5 
ma_energy <- 5 
kernel_func <- ma_gauss 
std_dev <- 1
upright_thresh <- 0.75
abs_acc_thresh <- 0.1 
thresh_abs <- 0.005 
thresh_rel <- 0.25 
min_step_period <- 5
max_step_period <- 40
period_len <- 5 
period_len_double <- 5
period_thresh <- 0.14
double_step_thresh <- 0.21
thresh_direction <- 0.3

data_0 <- fast_extraction_algorithm(df, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, 0, 0, 0, min_step_period, max_step_period, 7, 7, 0, 0, thresh_direction, sigma = std_dev) #Quite a bit of false negatives
data_1 <- fast_extraction_algorithm(df, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, 0.1, 0, 0.2, min_step_period, max_step_period, 6, 6, 0.05, 0.1, thresh_direction, sigma = std_dev) 
data_2 <- fast_extraction_algorithm(df, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, abs_acc_thresh, thresh_abs, thresh_rel, min_step_period, max_step_period, period_len, period_len_double, period_thresh, double_step_thresh, thresh_direction, sigma = std_dev)
data_3 <- fast_extraction_algorithm(df, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, 0.2, thresh_abs, thresh_rel, min_step_period, max_step_period, period_len, period_len_double, period_thresh, double_step_thresh, thresh_direction, sigma = std_dev)
data_4 <- fast_extraction_algorithm(df, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, 0.3, thresh_abs, thresh_rel, min_step_period, max_step_period, period_len, period_len_double, period_thresh, double_step_thresh, thresh_direction, sigma = std_dev)
data_5 <- fast_extraction_algorithm(df, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, 0.4, thresh_abs, thresh_rel, min_step_period, max_step_period, period_len, period_len_double, period_thresh, double_step_thresh, thresh_direction, sigma = std_dev)
data_6 <- fast_extraction_algorithm(df, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, 0.5, thresh_abs, thresh_rel, min_step_period, max_step_period, period_len, period_len_double, period_thresh, double_step_thresh, thresh_direction, sigma = std_dev)

#seq_list, time_thresh, freq_diff_thresh, min_total, wdw_size, min_highest, allow_small, hill_dominating_thresh, no_ma_fourier, kernel_fourier, ...
ordata_0 <- Glue_and_classify(data_0, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)
ordata_1 <- Glue_and_classify(data_1, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)
ordata_2 <- Glue_and_classify(data_2, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)
ordata_3 <- Glue_and_classify(data_3, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)
ordata_4 <- Glue_and_classify(data_4, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)
ordata_5 <- Glue_and_classify(data_5, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)
ordata_6 <- Glue_and_classify(data_6, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)
```

```{r}
pair_num <- 0
for(j in ordata_3){
  pair_num <- pair_num + length(j$cor_fw) + length(j$cor_bw)
}
pair_num
```


## Approach 1 + 2: getting all steps and average steps as before

```{r}
n <- 100
rescaled_data <- df_all_from_mvm_alt_nofilter_improved(ordata_3, n, min_square_difference_vert)

rescaled_data_alt <- df_all_from_mvm_alt_filter_improved(data = ordata_3, n = n, 
                                                         start_function = min_square_difference_vert)

rescaled_data <- df_all_from_mvm_alt_nofilter_improved_nocycle(data = ordata_3, n = n)
rescaled_data <- df_all_from_mvm_alt_filter_improved_nocycle(data = ordata_3, n = n)


rescaled_data_alt[[1]] %>% view()
#With selection step at front, such that we only compare with other steps with similar properties

```


```{r}
#Need to define a difference function, such as number of indices above certain difference! Or try squared difference and normal difference. Not getting logical output right now ... 
sumabsdiff <- function(seq1, seq2){
  return(sum(abs(seq1 - seq2)))
}
sumsquarediff <- function(seq1, seq2){
  return(sum(seq1 - seq2)^2)
}
idc_at_distance <- function(seq1, seq2){
  length(which(abs(seq1 - seq2) > 0.25))
}
max_distance <- function(seq1, seq2){
  max(abs(seq1 - seq2))
}

dist_function <- sumabsdiff

df <- as.data.frame(rescaled_data[[1]])
df_new <- df

diff_using_this_reference_fw <- numeric(nrow(df))

#Try all reference values i here !!!
for(i in 1:nrow(df)){
  print(i)
  rotations_list <- numeric(nrow(df))
  abs_diff_list <- numeric(nrow(df))

  reference <- unlist(df[i,])
  step_length <- length(reference)

  for(j in 1:nrow(df)){
    current_step <- unlist(df[j,])
    acc_differences <- numeric(step_length)
  
    acc_differences[1] <- dist_function(reference, current_step)
  
    for(k in 1:((step_length) - 1)){
      rotated <-  c(current_step[(k + 1):step_length], current_step[1:k])
      acc_differences[k+1] <- dist_function(reference, rotated)
    }
  
    best_rot <- which.min(acc_differences) - 1
    rotations_list[j] <- best_rot
    abs_diff_list[j] <- min(acc_differences)
  
    if(best_rot == 0){
      new_step <- current_step
      } else{
        new_step <- c(unlist(current_step)[(best_rot + 1):step_length],
                    unlist(current_step)[1:(best_rot)])
      }
    df_new[j,] <- new_step
  }
  
  diff_using_this_reference_fw[i] <- sum(abs_diff_list)

}

diff_using_this_reference_vert <- numeric(nrow(df))

for(i in 1:nrow(df)){
  print(i)
  df <- as.data.frame(rescaled_data[[2]])
  df_new <- df

  rotations_list <- numeric(nrow(df))
  abs_diff_list <- numeric(nrow(df))

  reference <- unlist(df[i,])
  step_length <- length(reference)

  for(j in 1:nrow(df)){
    current_step <- unlist(df[j,])
    acc_differences <- numeric(step_length)
  
    acc_differences[1] <- dist_function(reference, current_step)
  
    for(k in 1:((step_length) - 1)){
      rotated <-  c(current_step[(k + 1):step_length], current_step[1:k])
      acc_differences[k+1] <- dist_function(reference, current_step)
    }
  
    best_rot <- which.min(acc_differences) - 1
    rotations_list[j] <- best_rot
    abs_diff_list[j] <- min(acc_differences)
  
    if(best_rot == 0){
      new_step <- current_step
      } else{
        new_step <- c(unlist(current_step)[(best_rot + 1):step_length],
                    unlist(current_step)[1:(best_rot)])
      }
    df_new[j,] <- new_step
  }
  
  diff_using_this_reference_vert[i] <- sum(abs_diff_list)

}

  
#Now we know the differences every potential reference step gives, so we know the reference step that is most similar for having all other steps shifted

ref_index <- which.min(diff_using_this_reference_fw + diff_using_this_reference_vert)
```

```{r}
ref_index <- ref_index
three_dir_df <- list()
three_abs_diff_list <- list()

for(l in 1:3){
df <- as.data.frame(rescaled_data[[l]])
  df_new <- df

  rotations_list <- numeric(nrow(df))
  abs_diff_list <- numeric(nrow(df))

  reference <- unlist(df[ref_index,])
  step_length <- length(reference)

  for(j in 1:nrow(df)){
    current_step <- unlist(df[j,])
    acc_differences <- numeric(step_length)
  
    acc_differences[1] <- dist_function(reference, current_step)
  
    for(k in 1:((step_length) - 1)){
      rotated <-  c(current_step[(k + 1):step_length], current_step[1:k])
      acc_differences[k+1] <- dist_function(reference, rotated)
    }
  
    best_rot <- which.min(acc_differences) - 1
    rotations_list[j] <- best_rot
    abs_diff_list[j] <- min(acc_differences)
  
    if(best_rot == 0){
      new_step <- current_step
      } else{
        new_step <- c(unlist(current_step)[(best_rot + 1):step_length],
                    unlist(current_step)[1:(best_rot)])
      }
    df_new[j,] <- new_step
  }
  
  three_dir_df <- append(three_dir_df, list(df_new))
  three_abs_diff_list <- append(three_abs_diff_list, list(abs_diff_list))
}
```

## We only want to keep a certain fraction of the nicest steps now, where nice is compared to the mean where everything is shifted compared to the best reference point

```{r}
abs_diff_df <- three_dir_df[[2]] #fw versus vertical?!
df_nice_fw <- three_dir_df[[1]]
df_nice_vert <- three_dir_df[[2]]
df_nice_side <- three_dir_df[[3]]

#dist_function <- max_distance
#dist_function <- idc_at_distance
dist_function <- sumabsdiff
  
keep_per_step <- 0.95
iterations <- 2
alpha_val <- 0.2

for(i in 1:iterations){
  
  average_step <- colMeans(abs_diff_df)
  differences <- numeric(nrow(abs_diff_df))
  for(l in 1:nrow(abs_diff_df)){
    differences[l] <- dist_function(abs_diff_df[l,], average_step)
    }
  cutoff <- quantile(differences, keep_per_step)
  good_idc <- which(differences <= cutoff)
  df_nice_fw <- df_nice_fw[good_idc, ]
  df_nice_vert <- df_nice_vert[good_idc, ]
  df_nice_side <- df_nice_side[good_idc, ]
  
  abs_diff_df <- df_nice_vert #Or change to fw. Needed for next iteration
}


n <- ncol(df_nice_vert)
colour <- "#56B4E9" # "#D62728", "#FFCC33"
names <- c("Forward", "Vertical", "Sideways")
temp_df <- as.data.table(df_nice_fw)

colnames(temp_df) <- as.character(1:n)
temp_df$id <- 1:nrow(temp_df)
temp_melted = melt(temp_df, id.vars = 'id')
temp_means <- aggregate(value ~ variable, data = temp_melted, FUN = mean)
    
temp_melted$variable <- as.numeric(as.character(temp_melted$variable))
temp_means$variable <- as.numeric(as.character(temp_means$variable))
    
plot <- ggplot(temp_melted, aes(x = variable, y = value)) + 
      geom_line(aes(group = id), color = colour, linewidth = 0.05, alpha = alpha_val) +
      geom_line(data = temp_means, aes(x = variable, y = value, group = 1), 
                color = "black", linewidth = 0.5) +
      labs(
        x = "Index",
        y = TeX(r'( Acceleration in $m/s^2$ )'),
        title = paste0("Average step ", names[j])) +
      theme_minimal() +
      theme(
        text = element_text(size = 12),      
        axis.title = element_text(size = 12),   
        axis.text = element_text(size = 12),      
        legend.text = element_text(size = 12),     
        legend.title = element_text(size = 12),
        panel.background = element_rect(fill = "white", color = NA),
        plot.background = element_rect(fill = "white", color = NA),
        axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()
      )
plot
```

##Checking what steps of a person roughly look like

```{r}
for(j in 1:100){
  plot(unlist(three_dir_df[[2]][j,]), type = 'l')
}
```

## Selection at front: only comparing to other steps with a few key similar properties

```{r}

```

_____ _LINE OF NO RETURN_ ______

## After determining reference point: only keeping certain fraction of nicest steps

If possible storing them in same dataframe structure for quick plotting? Also determining average?

```{r}
abs_diff_list <- three_abs_diff_list[[2]] #fw versus vertical?!

frac_to_keep <- 0.1
alpha_val <- 0.3

cutoff <- quantile(abs_diff_list, frac_to_keep)
good_idc <- which(abs_diff_list <= cutoff)
df_nice_fw <- three_dir_df[[1]][good_idc, ]
df_nice_vert <- three_dir_df[[2]][good_idc, ]
df_nice_side <- three_dir_df[[3]][good_idc, ]

n <- ncol(df_nice_fw)
colour <- "#56B4E9" # "#D62728", "#FFCC33"
names <- c("Forward", "Vertical", "Sideways")
temp_df <- as.data.table(df_nice_vert)

colnames(temp_df) <- as.character(1:n)
temp_df$id <- 1:nrow(temp_df)
temp_melted = melt(temp_df, id.vars = 'id')
temp_means <- aggregate(value ~ variable, data = temp_melted, FUN = mean)
    
temp_melted$variable <- as.numeric(as.character(temp_melted$variable))
temp_means$variable <- as.numeric(as.character(temp_means$variable))
    
plot <- ggplot(temp_melted, aes(x = variable, y = value)) + 
      geom_line(aes(group = id), color = colour, linewidth = 0.05, alpha = alpha_val) +
      geom_line(data = temp_means, aes(x = variable, y = value, group = 1), 
                color = "black", linewidth = 0.5) +
      labs(
        x = "Index",
        y = TeX(r'( Acceleration in $m/s^2$ )'),
        title = paste0("Average step ", names[j])) +
      theme_minimal() +
      theme(
        text = element_text(size = 12),      
        axis.title = element_text(size = 12),   
        axis.text = element_text(size = 12),      
        legend.text = element_text(size = 12),     
        legend.title = element_text(size = 12),
        panel.background = element_rect(fill = "white", color = NA),
        plot.background = element_rect(fill = "white", color = NA),
        axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()
      )
plot
```

```{r}
for(j in 100:200){
  plot(unlist(three_dir_df[[2]][j,]), type = 'l')
}
```

## Selection at front: only comparing with those with similar properties



## Approach 2 failed attempt:
```{r}
test_fw <- align_steps_fft(as.matrix(rescaled_data[[1]]), iterations = 1)
test_vert <- align_steps_fft(as.matrix(rescaled_data[[2]]), iterations = 1)
test_fw$rotations
test_vert$rotations

align_steps_fft <- function(steps_matrix, iterations = 1) {
  n_steps <- nrow(steps_matrix)
  step_length <- ncol(steps_matrix)
  aligned_matrix <- steps_matrix
  rotations <- integer(n_steps)

  reference <- steps_matrix[1, ]  

  for (iter in 1:iterations) {
    fft_ref <- fft(reference)

    for (i in 1:n_steps) {
      sequence <- aligned_matrix[i, ]
      fft_seq <- fft(sequence)

      cross_corr <- Re(fft(fft_ref * Conj(fft_seq), inverse = TRUE))
      best_shift <- which.max(cross_corr) - 1

      # Rotate the sequence
      if (best_shift == 0) {
        rotated <- sequence
        } else {
          rotated <- c(sequence[(best_shift + 1):step_length], sequence[1:best_shift])
          }
      aligned_matrix[i, ] <- rotated

      # Track rotation
      if (iter == 1) {
        rotations[i] <- best_shift
      } else {
        rotations[i] <- (rotations[i] + best_shift) %% step_length
      }
    }

    # Update reference for next iteration
    reference <- aligned_matrix[1, ]
    if (n_steps > 1) {
      reference <- colMeans(aligned_matrix)
    }
  }

  return(list(aligned = aligned_matrix, rotations = rotations))
}
```

## Approach 3: same approach with certain fraction of steps thrown out. Only the one that fit most nicely

```{r}

```

## Approach 3: Aligning steps to make them as similar as possible before getting average

```{r}

```

## Approach 4: Splitting up steps into categories before computing average etc.

```{r}

```