```{r, message=F, warning=F}
#Data analysis
library(tidyverse)
library(latex2exp)
library(patchwork)
library(scales)
library(RColorBrewer)

#Working with the activity class and data files
library(lubridate)
library(read.gt3x)
library(PhysicalActivity)

#Solving equations
library(nleqslv)
library(pracma)
library(latex2exp)

#Reshaping / data manipulation
library(reshape2)
library(data.table)
library(zeallot)

##gganimate/creating animations
library(gganimate)
library(glue)
library(shiny)
library(av)
library(magick)

#Clustering
library(dbscan)
library(cluster)
library(plotly)
library(htmlwidgets)
library(htmltools)
```

# Examples all with spasm data, later generalise for more data after getting approach

## General: data

```{r}
#Purely analysis of what is on video (5 seconds on both sides):
start_time <- as.POSIXct("2025-04-15 11:34:52.099999")
end_time <- as.POSIXct("2025-04-15 11:35:51.099999")
df_spas_vid <- filter(Misc3, time > start_time & time < end_time)

start_time <- as.POSIXct("2025-01-20 10:31:00.266666")
end_time <- as.POSIXct("2025-01-20 10:39:28.266666")
df_walk1 <- filter(Walk1, time > start_time & time < end_time)

start_time <- as.POSIXct("2025-01-20 10:55:00.266666")
end_time <- as.POSIXct("2025-01-20 11:03:28.266666")
df_walk2 <- filter(Walk1, time > start_time & time < end_time)

start_time <- as.POSIXct("2025-01-20 11:36:00.266666")
end_time <- as.POSIXct("2025-01-20 11:44:28.266666")
df_walk3 <- filter(Walk1, time > start_time & time < end_time)

start_time <- as.POSIXct("2025-01-20 14:24:00.266666")
end_time <- as.POSIXct("2025-01-20 14:32:28.266666")
df_walk4 <- filter(Walk2, time > start_time & time < end_time)

start_time <- as.POSIXct("2025-01-20 14:59:00.266666")
end_time <- as.POSIXct("2025-01-20 15:08:28.266666")
df_walk5 <- filter(Walk2, time > start_time & time < end_time)

start_time <- as.POSIXct("2025-01-20 15:37:28.266666")
end_time <- as.POSIXct("2025-01-20 15:45:28.266666")
df_walk6 <- filter(Walk2, time > start_time & time < end_time)

start_time <- as.POSIXct("2025-02-17 10:42:00.266666")
end_time <- as.POSIXct("2025-02-17 10:51:28.266666")
df_walk7 <- filter(Walk3, time > start_time & time < end_time)

start_time <- as.POSIXct("2025-02-17 11:15:00.266666")
end_time <- as.POSIXct("2025-02-17 11:24:28.266666")
df_walk8 <- filter(Walk3, time > start_time & time < end_time)

start_time <- as.POSIXct("2025-02-17 11:46:00.266666")
end_time <- as.POSIXct("2025-02-17 11:54:28.266666")
df_walk9 <- filter(Walk3, time > start_time & time < end_time)

start_time <- as.POSIXct("2025-02-17 13:34:00.266666")
end_time <- as.POSIXct("2025-02-17 13:43:28.266666")
df_walk10 <- filter(Walk3, time > start_time & time < end_time)

wdw_size <- 120
ma_data <- 5 
ma_energy <- 5 
kernel_func <- ma_gauss 
std_dev <- 1
upright_thresh <- 0.75
abs_acc_thresh <- 0.2 
thresh_abs <- 0 
thresh_rel <- 0.25 
min_step_period <- 5
max_step_period <- 40
period_len <- 5 
period_len_double <- 5
period_thresh <- 0.14
double_step_thresh <- 0.21
thresh_direction <- 0.3

# data_0 <- fast_extraction_algorithm(df, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, 0, 0, 0, min_step_period, max_step_period, 7, 7, 0, 0, thresh_direction, sigma = std_dev) #Quite a bit of false negatives
# data_1 <- fast_extraction_algorithm(df, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, 0.1, 0, 0.2, min_step_period, max_step_period, 6, 6, 0.05, 0.1, thresh_direction, sigma = std_dev) 
# data_2 <- fast_extraction_algorithm(df, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, 0.1, thresh_abs, thresh_rel, min_step_period, max_step_period, period_len, period_len_double, period_thresh, double_step_thresh, thresh_direction, sigma = std_dev)
data_walk1 <- fast_extraction_algorithm(df_walk1, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, abs_acc_thresh, thresh_abs, thresh_rel, min_step_period, max_step_period, period_len, period_len_double, period_thresh, double_step_thresh, thresh_direction, sigma = std_dev)
# data_4 <- fast_extraction_algorithm(df, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, 0.3, thresh_abs, thresh_rel, min_step_period, max_step_period, period_len, period_len_double, period_thresh, double_step_thresh, thresh_direction, sigma = std_dev)
# data_5 <- fast_extraction_algorithm(df, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, 0.4, thresh_abs, thresh_rel, min_step_period, max_step_period, period_len, period_len_double, period_thresh, double_step_thresh, thresh_direction, sigma = std_dev)
# data_6 <- fast_extraction_algorithm(df, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, 0.5, thresh_abs, thresh_rel, min_step_period, max_step_period, period_len, period_len_double, period_thresh, double_step_thresh, thresh_direction, sigma = std_dev)

#seq_list, time_thresh, freq_diff_thresh, min_total, wdw_size, min_highest, allow_small, hill_dominating_thresh, no_ma_fourier, kernel_fourier, ...
# ordata_0 <- Glue_and_classify(data_0, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)
# ordata_1 <- Glue_and_classify(data_1, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)
# ordata_2 <- Glue_and_classify(data_2, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)
# ordata_3 <- Glue_and_classify(data_walk1, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)
# ordata_4 <- Glue_and_classify(data_4, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)
# ordata_5 <- Glue_and_classify(data_5, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)
# ordata_6 <- Glue_and_classify(data_6, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)

data_walk2 <- fast_extraction_algorithm(df_walk2, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, abs_acc_thresh, thresh_abs, thresh_rel, min_step_period, max_step_period, period_len, period_len_double, period_thresh, double_step_thresh, thresh_direction, sigma = std_dev)
data_walk3 <- fast_extraction_algorithm(df_walk3, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, abs_acc_thresh, thresh_abs, thresh_rel, min_step_period, max_step_period, period_len, period_len_double, period_thresh, double_step_thresh, thresh_direction, sigma = std_dev)
data_walk4 <- fast_extraction_algorithm(df_walk4, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, abs_acc_thresh, thresh_abs, thresh_rel, min_step_period, max_step_period, period_len, period_len_double, period_thresh, double_step_thresh, thresh_direction, sigma = std_dev)
data_walk5 <- fast_extraction_algorithm(df_walk5, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, abs_acc_thresh, thresh_abs, thresh_rel, min_step_period, max_step_period, period_len, period_len_double, period_thresh, double_step_thresh, thresh_direction, sigma = std_dev)
data_walk6 <- fast_extraction_algorithm(df_walk6, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, abs_acc_thresh, thresh_abs, thresh_rel, min_step_period, max_step_period, period_len, period_len_double, period_thresh, double_step_thresh, thresh_direction, sigma = std_dev)
data_walk7 <- fast_extraction_algorithm(df_walk7, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, abs_acc_thresh, thresh_abs, thresh_rel, min_step_period, max_step_period, period_len, period_len_double, period_thresh, double_step_thresh, thresh_direction, sigma = std_dev)
data_walk8 <- fast_extraction_algorithm(df_walk8, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, abs_acc_thresh, thresh_abs, thresh_rel, min_step_period, max_step_period, period_len, period_len_double, period_thresh, double_step_thresh, thresh_direction, sigma = std_dev)
data_walk9 <- fast_extraction_algorithm(df_walk9, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, abs_acc_thresh, thresh_abs, thresh_rel, min_step_period, max_step_period, period_len, period_len_double, period_thresh, double_step_thresh, thresh_direction, sigma = std_dev)
data_walk10 <- fast_extraction_algorithm(df_walk10, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, abs_acc_thresh, thresh_abs, thresh_rel, min_step_period, max_step_period, period_len, period_len_double, period_thresh, double_step_thresh, thresh_direction, sigma = std_dev)

#4 variants for those with little data as well
data_walk2_low <- fast_extraction_algorithm(df_walk2, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, 0, thresh_abs, 0, min_step_period, max_step_period, period_len, period_len_double, period_thresh, double_step_thresh, thresh_direction, sigma = std_dev)
data_walk3_low <- fast_extraction_algorithm(df_walk3, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, 0, thresh_abs, 0, min_step_period, max_step_period, period_len, period_len_double, period_thresh, double_step_thresh, thresh_direction, sigma = std_dev)
data_walk4_low <- fast_extraction_algorithm(df_walk4, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, 0, thresh_abs, 0, min_step_period, max_step_period, period_len, period_len_double, 0.14, 0.14, thresh_direction, sigma = std_dev)
data_walk5_low <- fast_extraction_algorithm(df_walk5, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, 0, thresh_abs, 0, min_step_period, max_step_period, period_len, period_len_double, period_thresh, double_step_thresh, thresh_direction, sigma = std_dev)

#We also add a few hundred steps for the healthy children
start_time <- as.POSIXct("2024-01-06 07:00:00.000")
end_time <- as.POSIXct("2024-01-06 09:00:00.000")
df_H10 <- filter(H10_off, time > start_time & time < end_time)
data_H10 <- fast_extraction_algorithm(df_H10, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, abs_acc_thresh, thresh_abs, thresh_rel, min_step_period, max_step_period, period_len, period_len_double, period_thresh, double_step_thresh, thresh_direction, sigma = std_dev)

start_time <- as.POSIXct("2024-01-06 09:40:00.000") #Opted for slightly later because then more activity and less time needed to wait
end_time <- as.POSIXct("2024-01-06 10:00:00.000")
df_H11 <- filter(H11_off, time > start_time & time < end_time)
data_H11 <- fast_extraction_algorithm(df_H11, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, abs_acc_thresh, thresh_abs, thresh_rel, min_step_period, max_step_period, period_len, period_len_double, period_thresh, double_step_thresh, thresh_direction, sigma = std_dev)

start_time <- as.POSIXct("2024-06-13 08:00:00.000")
end_time <- as.POSIXct("2024-06-13 09:00:00.000")
df_H12 <- filter(H12_off, time > start_time & time < end_time)
data_H12 <- fast_extraction_algorithm(df_H12, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, abs_acc_thresh, thresh_abs, thresh_rel, min_step_period, max_step_period, period_len, period_len_double, period_thresh, double_step_thresh, thresh_direction, sigma = std_dev)

start_time <- as.POSIXct("2024-03-12 08:00:00.000")
end_time <- as.POSIXct("2024-03-12 09:00:00.000")
df_H13 <- filter(H13_off, time > start_time & time < end_time)
data_H13 <- fast_extraction_algorithm(df_H13, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, abs_acc_thresh, thresh_abs, thresh_rel, min_step_period, max_step_period, period_len, period_len_double, period_thresh, double_step_thresh, thresh_direction, sigma = std_dev)

start_time <- as.POSIXct("2024-03-12 09:50.000")
end_time <- as.POSIXct("2024-03-12 10:20:00.000")
df_H14 <- filter(H14_off, time > start_time & time < end_time)
data_H14 <- fast_extraction_algorithm(df_H14, wdw_size, ma_data, ma_energy, kernel_func, upright_thresh, abs_acc_thresh, thresh_abs, thresh_rel, min_step_period, max_step_period, period_len, period_len_double, period_thresh, double_step_thresh, thresh_direction, sigma = std_dev)

data <- data_H14
total_steps <- 0
for(j in data){
  mvm_steps <- max(j$data$in_step_fw) + max(j$data$in_step_bw)
  total_steps <- total_steps + mvm_steps 
}
total_steps
```

```{r}
ordata_walk1 <- Glue_and_classify(data_walk1, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)
ordata_walk2 <- Glue_and_classify(data_walk2, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)
ordata_walk3 <- Glue_and_classify(data_walk3, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)
ordata_walk4 <- Glue_and_classify(data_walk4, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)
ordata_walk5 <- Glue_and_classify(data_walk5, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)
ordata_walk6 <- Glue_and_classify(data_walk6, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)
ordata_walk7 <- Glue_and_classify(data_walk7, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)
ordata_walk8 <- Glue_and_classify(data_walk8, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)
ordata_walk9 <- Glue_and_classify(data_walk9, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)
ordata_walk10 <- Glue_and_classify(data_walk10, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)

ordata_walk2_low <- Glue_and_classify(data_walk2_low, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)
ordata_walk3_low <- Glue_and_classify(data_walk3_low, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)
ordata_walk4_low <- Glue_and_classify(data_walk4_low, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)
ordata_walk5_low <- Glue_and_classify(data_walk5_low, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)

ordata_H10 <- Glue_and_classify(data_H10, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)
ordata_H11 <- Glue_and_classify(data_H11, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)
ordata_H12 <- Glue_and_classify(data_H12, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)
ordata_H13 <- Glue_and_classify(data_H13, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)
ordata_H14 <- Glue_and_classify(data_H14, 3, 3, 150, 150, 150, T, 20, 5, ma_gauss, sigma = 1)
```

## Filter functions
```{r}
filter_example <- function(mvm){
  if((mvm$main_freq < 15) & (mvm$movement_type != "Cycle")){
    return(T)
  } else{
    return(F)
  }
}

filter_none <- function(mvm){
  return(T)
}

filter_cycling <- function(mvm){
  if(mvm$movement_type != "Cycle"){
    return(T)
  } else{
    return(F)
  }
}
```

## Distance functions
```{r}
sumabsdiff <- function(seq1, seq2){
  return(sum(abs(seq1 - seq2)))
}
sumsquarediff <- function(seq1, seq2){
  return(sum(seq1 - seq2)^2)
}
idc_at_distance <- function(seq1, seq2){
  length(which(abs(seq1 - seq2) > 0.25))
}
max_distance <- function(seq1, seq2){
  max(abs(seq1 - seq2))
}

#Invariant distance functions
sign_disagree <- function(seq1, seq2){
  sum(sign(seq1) != sign(seq2))
}

peak_height <- function(seq1, seq2){
  return(abs(max(abs(seq1)) - max(abs(seq2))))
}

cosine_similarity <- function(seq1, seq2){
  return(1 - (sum(seq1 * seq2)) / ((sqrt(sum(seq1^2)) * sqrt(sum(seq2^2)))))
}

correlation_distance <- function(seq1, seq2){
  return(1 - cor(seq1, seq2))
}

sumabsscaled <- function(seq1, seq2){
  diff <- sum(abs(seq1 - seq2))
  return(diff/(mean(abs(seq1))/2 + mean(abs(seq2))/2)) 
  #If one value is twice as high everywhere would need to divide by two
  #No problem that it is not perfect/constant no problem if we choose robust parameters
}

#Old invariant distance functions

sumabsdiffpercentage <- function(seq1, seq2){ #So puts more weight on differences at low values than at high values
  return(sum(abs(seq1 - seq2)/(abs(seq1)/2 + abs(seq2)/2)))
}
  
rescaled_sumabsdiff <- function(seq1, seq2){
  seq1s <- scale(seq1, center = T, scale = T)
  seq2s <- scale(seq2, center = T, scale = T)
  sum_abs_diff <- sum(abs(seq1s - seq2s))
  return(sum_abs_diff)
}

rescaled_sumsquared <- function(seq1, seq2){
  seq1s <- scale(seq1, center = T, scale = T)
  seq2s <- scale(seq2, center = T, scale = T)
  sum_abs_diff <- sum((seq1s - seq2s)^2)
  return(sum_abs_diff)
}

#Alternatives should take some parameter that depends on the data for it to be invariant!
```

## Actual code ``short version''

```{r}
short_dataframes_walk1 <- full_steps(ordata_walk1, 80, filter_none)
short_dataframes_walk2 <- full_steps(ordata_walk2_low, 80, filter_none) #Mind the low
short_dataframes_walk3 <- full_steps(ordata_walk3_low, 80, filter_none) #Mind the low
short_dataframes_walk4 <- full_steps(ordata_walk4_low, 80, filter_none) #Mind the low
short_dataframes_walk5 <- full_steps(ordata_walk5_low, 80, filter_none) #Mind the low
short_dataframes_walk6 <- full_steps(ordata_walk6, 80, filter_none)
short_dataframes_walk7 <- full_steps(ordata_walk7, 80, filter_none)
short_dataframes_walk8 <- full_steps(ordata_walk8, 80, filter_none)
short_dataframes_walk9 <- full_steps(ordata_walk9, 80, filter_none)
short_dataframes_walk10 <- full_steps(ordata_walk10, 80, filter_none)

short_distance_data_walk1_sgn <- full_groups(short_dataframes_walk1[[2]], sign_disagree)
short_distance_data_walk2_sgn <- full_groups(short_dataframes_walk2[[2]], sign_disagree)
short_distance_data_walk3_sgn <- full_groups(short_dataframes_walk3[[2]], sign_disagree)
short_distance_data_walk4_sgn <- full_groups(short_dataframes_walk4[[2]], sign_disagree)
short_distance_data_walk5_sgn <- full_groups(short_dataframes_walk5[[2]], sign_disagree)
short_distance_data_walk6_sgn <- full_groups(short_dataframes_walk6[[2]], sign_disagree)
short_distance_data_walk7_sgn <- full_groups(short_dataframes_walk7[[2]], sign_disagree)
short_distance_data_walk8_sgn <- full_groups(short_dataframes_walk8[[2]], sign_disagree)
short_distance_data_walk9_sgn <- full_groups(short_dataframes_walk9[[2]], sign_disagree)
short_distance_data_walk10_sgn <- full_groups(short_dataframes_walk10[[2]], sign_disagree)

short_distance_data_walk1_peak <- full_groups(short_dataframes_walk1[[2]], peak_height)
short_distance_data_walk2_peak <- full_groups(short_dataframes_walk2[[2]], peak_height)
short_distance_data_walk3_peak <- full_groups(short_dataframes_walk3[[2]], peak_height)
short_distance_data_walk4_peak <- full_groups(short_dataframes_walk4[[2]], peak_height)
short_distance_data_walk5_peak <- full_groups(short_dataframes_walk5[[2]], peak_height)
short_distance_data_walk6_peak <- full_groups(short_dataframes_walk6[[2]], peak_height)
short_distance_data_walk7_peak <- full_groups(short_dataframes_walk7[[2]], peak_height)
short_distance_data_walk8_peak <- full_groups(short_dataframes_walk8[[2]], peak_height)
short_distance_data_walk9_peak <- full_groups(short_dataframes_walk9[[2]], peak_height)
short_distance_data_walk10_peak <- full_groups(short_dataframes_walk10[[2]], peak_height)

short_distance_data_walk1_cos <- full_groups(short_dataframes_walk1[[2]], cosine_similarity)
short_distance_data_walk2_cos <- full_groups(short_dataframes_walk2[[2]], cosine_similarity)
short_distance_data_walk3_cos <- full_groups(short_dataframes_walk3[[2]], cosine_similarity)
short_distance_data_walk4_cos <- full_groups(short_dataframes_walk4[[2]], cosine_similarity)
short_distance_data_walk5_cos <- full_groups(short_dataframes_walk5[[2]], cosine_similarity)
short_distance_data_walk6_cos <- full_groups(short_dataframes_walk6[[2]], cosine_similarity)
short_distance_data_walk7_cos <- full_groups(short_dataframes_walk7[[2]], cosine_similarity)
short_distance_data_walk8_cos <- full_groups(short_dataframes_walk8[[2]], cosine_similarity)
short_distance_data_walk9_cos <- full_groups(short_dataframes_walk9[[2]], cosine_similarity)
short_distance_data_walk10_cos <- full_groups(short_dataframes_walk10[[2]], cosine_similarity)

short_distance_data_walk1_cor <- full_groups(short_dataframes_walk1[[2]], correlation_distance)
short_distance_data_walk2_cor <- full_groups(short_dataframes_walk2[[2]], correlation_distance)
short_distance_data_walk3_cor <- full_groups(short_dataframes_walk3[[2]], correlation_distance)
short_distance_data_walk4_cor <- full_groups(short_dataframes_walk4[[2]], correlation_distance)
short_distance_data_walk5_cor <- full_groups(short_dataframes_walk5[[2]], correlation_distance)
short_distance_data_walk6_cor <- full_groups(short_dataframes_walk6[[2]], correlation_distance)
short_distance_data_walk7_cor <- full_groups(short_dataframes_walk7[[2]], correlation_distance)
short_distance_data_walk8_cor <- full_groups(short_dataframes_walk8[[2]], correlation_distance)
short_distance_data_walk9_cor <- full_groups(short_dataframes_walk9[[2]], correlation_distance)
short_distance_data_walk10_cor <- full_groups(short_dataframes_walk10[[2]], correlation_distance)

short_distance_data_walk1_sas <- full_groups(short_dataframes_walk1[[2]], sumabsscaled)
short_distance_data_walk2_sas <- full_groups(short_dataframes_walk2[[2]], sumabsscaled)
short_distance_data_walk3_sas <- full_groups(short_dataframes_walk3[[2]], sumabsscaled)
short_distance_data_walk4_sas <- full_groups(short_dataframes_walk4[[2]], sumabsscaled)
short_distance_data_walk5_sas <- full_groups(short_dataframes_walk5[[2]], sumabsscaled)
short_distance_data_walk6_sas <- full_groups(short_dataframes_walk6[[2]], sumabsscaled)
short_distance_data_walk7_sas <- full_groups(short_dataframes_walk7[[2]], sumabsscaled)
short_distance_data_walk8_sas <- full_groups(short_dataframes_walk8[[2]], sumabsscaled)
short_distance_data_walk9_sas <- full_groups(short_dataframes_walk9[[2]], sumabsscaled)
short_distance_data_walk10_sas <- full_groups(short_dataframes_walk10[[2]], sumabsscaled)
```

Visualisation
```{r}
names <- c("Rocco", "Pleun", "Estelle", "Emma", "Elvira", "Sverre", "Devin", "Gerwin", "Roel", "Mike")
no_to_compare_half <- 30

for(j in 1:10){
  clustering <- c()
  data <- get(paste0("short_distance_data_walk", j, "_sas"))
  D <- data[[1]]
  density <- 70
  points <- 6
  
  print((noise_frac <- sum(dbscan(as.dist(D), density, points)$clust == 0)/nrow(D)))
  # print(nrow(D))
  
  clustering <- numeric(nrow(D))
  for(k in 1:nrow(D)){
    if(k > nrow(D) - no_to_compare_half){
      max_idx <- nrow(D)
      min_idx <- nrow(D) - 2*no_to_compare_half
    } else if(k < (no_to_compare_half + 1)){
      max_idx <- no_to_compare_half * 2 + 1
      min_idx <- 1
    } else{
      min_idx <- k - no_to_compare_half
      max_idx <- k + no_to_compare_half
    }
  close_points <- 0
  for(l in min_idx:max_idx){
    if(D[k, l] < density){
      close_points <- close_points + 1 #Always close to itself
    }
  }
  if(close_points > points){
    clustering[k] <- 1
  } else{
    clustering[k] <- 0
  }
  }
  
  mds_result <- cmdscale(as.dist(D), k = 3, eig = T)
  
  coords <- as.data.frame(mds_result$points)
  colnames(coords) <- c("X", "Y", "Z")
  
  coords$cluster <- clustering
  coords$cluster <- factor(coords$cluster, levels = c(0, 1), labels = c("Noise", "Clustered"))
  
  assign(paste0("sas_walk", j) , plot_ly(coords, x = ~X, y = ~Y, z = ~Z, color = ~cluster,
        type = 'scatter3d', mode = 'markers',
        marker = list(size = 4)) %>%
         layout(title = paste0("Absolute rescaled sum of differences in vertical acceleration, ", names[j]),
                legend = list(title = list(text = "Group"))))
}


for(j in 1:10){
  clustering <- c()
  data <- get(paste0("short_distance_data_walk", j, "_sgn"))
  D <- data[[1]]
  density <- 15
  points <- 6
  
  # print((noise_frac <- sum(dbscan(as.dist(D), density, points)$clust == 0)/nrow(D)))
  # print(nrow(D))
  
  clustering <- numeric(nrow(D))
  for(k in 1:nrow(D)){
    if(k > nrow(D) - no_to_compare_half){
      max_idx <- nrow(D)
      min_idx <- nrow(D) - 2*no_to_compare_half
    } else if(k < (no_to_compare_half + 1)){
      max_idx <- no_to_compare_half * 2 + 1
      min_idx <- 1
    } else{
      min_idx <- k - no_to_compare_half
      max_idx <- k + no_to_compare_half
    }
  close_points <- 0
  for(l in min_idx:max_idx){
    if(D[k, l] < density){
      close_points <- close_points + 1 #Always close to itself
    }
  }
  if(close_points > points){
    clustering[k] <- 1
  } else{
    clustering[k] <- 0
  }
  }
  
  print(sum(clustering == 0)/length(clustering))
  
  mds_result <- cmdscale(as.dist(D), k = 3, eig = T)
  
  coords <- as.data.frame(mds_result$points)
  colnames(coords) <- c("X", "Y", "Z")
  
  coords$cluster <- clustering
  coords$cluster <- factor(coords$cluster, levels = c(0, 1), labels = c("Noise", "Clustered"))
  
  assign(paste0("sgn_walk", j) , plot_ly(coords, x = ~X, y = ~Y, z = ~Z, color = ~cluster,
        type = 'scatter3d', mode = 'markers',
        marker = list(size = 4)) %>%
         layout(title = paste0("Differences in sign in vertical acceleration, ", names[j]),
                legend = list(title = list(text = "Group"))))
}

for(j in 1:10){
  clustering <- c()
  data <- get(paste0("short_distance_data_walk", j, "_cor"))
  D <- data[[1]]
  density <- 0.32
  points <- 6
  
  # print((noise_frac <- sum(dbscan(as.dist(D), density, points)$clust == 0)/nrow(D)))
  # print(nrow(D))
  
  clustering <- numeric(nrow(D))
  for(k in 1:nrow(D)){
    if(k > nrow(D) - no_to_compare_half){
      max_idx <- nrow(D)
      min_idx <- nrow(D) - 2*no_to_compare_half
    } else if(k < (no_to_compare_half + 1)){
      max_idx <- no_to_compare_half * 2 + 1
      min_idx <- 1
    } else{
      min_idx <- k - no_to_compare_half
      max_idx <- k + no_to_compare_half
    }
  close_points <- 0
  for(l in min_idx:max_idx){
    if(D[k, l] < density){
      close_points <- close_points + 1 #Always close to itself
    }
  }
  if(close_points > points){
    clustering[k] <- 1
  } else{
    clustering[k] <- 0
  }
  }
  
  print(sum(clustering == 0)/length(clustering))
  
  mds_result <- cmdscale(as.dist(D), k = 3, eig = T)
  
  coords <- as.data.frame(mds_result$points)
  colnames(coords) <- c("X", "Y", "Z")
  
  coords$cluster <- clustering
  coords$cluster <- factor(coords$cluster, levels = c(0, 1), labels = c("Noise", "Clustered"))
  
  assign(paste0("cor_walk", j) , plot_ly(coords, x = ~X, y = ~Y, z = ~Z, color = ~cluster,
        type = 'scatter3d', mode = 'markers',
        marker = list(size = 4)) %>%
         layout(title = paste0("Differences in correlation in vertical acceleration, ", names[j]),
                legend = list(title = list(text = "Group"))))
}

for(j in 1:10){
  clustering <- c()
  data <- get(paste0("short_distance_data_walk", j, "_cos"))
  D <- data[[1]]
  density <- 0.4
  points <- 6
  
  # print((noise_frac <- sum(dbscan(as.dist(D), density, points)$clust == 0)/nrow(D)))
  # print(nrow(D))
  
  clustering <- numeric(nrow(D))
  for(k in 1:nrow(D)){
    if(k > nrow(D) - no_to_compare_half){
      max_idx <- nrow(D)
      min_idx <- nrow(D) - 2*no_to_compare_half
    } else if(k < (no_to_compare_half + 1)){
      max_idx <- no_to_compare_half * 2 + 1
      min_idx <- 1
    } else{
      min_idx <- k - no_to_compare_half
      max_idx <- k + no_to_compare_half
    }
  close_points <- 0
  for(l in min_idx:max_idx){
    if(D[k, l] < density){
      close_points <- close_points + 1 #Always close to itself
    }
  }
  if(close_points > points){
    clustering[k] <- 1
  } else{
    clustering[k] <- 0
  }
  }
  
  print(sum(clustering == 0)/length(clustering))
  
  mds_result <- cmdscale(as.dist(D), k = 3, eig = T)
  
  coords <- as.data.frame(mds_result$points)
  colnames(coords) <- c("X", "Y", "Z")
  
  coords$cluster <- clustering
  coords$cluster <- factor(coords$cluster, levels = c(0, 1), labels = c("Noise", "Clustered"))
  
  assign(paste0("cos_walk", j) , plot_ly(coords, x = ~X, y = ~Y, z = ~Z, color = ~cluster,
        type = 'scatter3d', mode = 'markers',
        marker = list(size = 4)) %>%
         layout(title = paste0("Differences in cosine similarity in vertical acceleration, ", names[j]),
                legend = list(title = list(text = "Group"))))
}

for(j in 1:10){
  clustering <- c()
  data <- get(paste0("short_distance_data_walk", j, "_peak"))
  D <- data[[1]]
  density <- 0.25
  points <- 6
  
  #print((noise_frac <- sum(dbscan(as.dist(D), density, points)$clust == 0)/nrow(D)))
  # print(nrow(D))
  
  clustering <- numeric(nrow(D))
  for(k in 1:nrow(D)){
    if(k > nrow(D) - no_to_compare_half){
      max_idx <- nrow(D)
      min_idx <- nrow(D) - 2*no_to_compare_half
    } else if(k < (no_to_compare_half + 1)){
      max_idx <- no_to_compare_half * 2 + 1
      min_idx <- 1
    } else{
      min_idx <- k - no_to_compare_half
      max_idx <- k + no_to_compare_half
    }
  close_points <- 0
  for(l in min_idx:max_idx){
    if(D[k, l] < density){
      close_points <- close_points + 1 #Always close to itself
    }
  }
  if(close_points > points){
    clustering[k] <- 1
  } else{
    clustering[k] <- 0
  }
  }
  
  print(sum(clustering == 0)/length(clustering))
  
  mds_result <- cmdscale(as.dist(D), k = 3, eig = T)
  
  coords <- as.data.frame(mds_result$points)
  colnames(coords) <- c("X", "Y", "Z")
  
  coords$cluster <- clustering
  coords$cluster <- factor(coords$cluster, levels = c(0, 1), labels = c("Noise", "Clustered"))
  
  assign(paste0("peak_walk", j) , plot_ly(coords, x = ~X, y = ~Y, z = ~Z, color = ~cluster,
        type = 'scatter3d', mode = 'markers',
        marker = list(size = 4)) %>%
         layout(title = paste0("Differences in absolute maximum of vertical acceleration. Note scale on axes: n = nanounits from rounding, data is a one-dimensional test case, ", names[j]),
                legend = list(title = list(text = "Group"))))
}


for (i in 1:10) {
    plots <- list()
    plots <- c(plots, list(
      get(paste0("sas_walk", i)),
      get(paste0("cor_walk", i)),
      get(paste0("cos_walk", i)),
      get(paste0("peak_walk", i)),
      get(paste0("sgn_walk", i))
    ))
 saveWidget(browsable(tagList(plots)), 
           paste0("walk_plots_", names[i], ".html"), 
           selfcontained = TRUE)
}

for(i in 1:10){
  for(j in c("sas", "cor", "cos", "peak", "sgn")){
    plot <- get(paste0(j, "_walk", i))
    saveWidget(plot, paste0(j, "_", names[i], ".html"), selfcontained = T)
  }
}

```

## Actual code (older version)
```{r}
dataframes_walk1 <- full_steps_old(ordata_walk1, 200, filter_none)
dataframes_walk2 <- full_steps_old(ordata_walk2, 200, filter_none)
dataframes_walk3 <- full_steps_old(ordata_walk3, 200, filter_none)
dataframes_walk4 <- full_steps_old(ordata_walk4, 200, filter_none)
dataframes_walk5 <- full_steps_old(ordata_walk5, 200, filter_none)
dataframes_walk6 <- full_steps_old(ordata_walk6, 200, filter_none)
dataframes_walk7 <- full_steps_old(ordata_walk7, 200, filter_none)
dataframes_walk8 <- full_steps_old(ordata_walk8, 200, filter_none)
dataframes_walk9 <- full_steps_old(ordata_walk9, 200, filter_none)
dataframes_walk10 <- full_steps_old(ordata_walk10, 200, filter_none)
dataframes_walk2_low <- full_steps_old(ordata_walk2_low, 200, filter_none)
dataframes_walk3_low <- full_steps_old(ordata_walk3_low, 200, filter_none)
dataframes_walk4_low <- full_steps_old(ordata_walk4_low, 200, filter_none)
dataframes_walk5_low <- full_steps_old(ordata_walk5_low, 200, filter_none)
dataframes_H10 <- full_steps_old(ordata_H10, 200, filter_none)
dataframes_H11 <- full_steps_old(ordata_H11, 200, filter_none)
dataframes_H12 <- full_steps_old(ordata_H12, 200, filter_none)
dataframes_H13 <- full_steps_old(ordata_H13, 200, filter_none)
dataframes_H14 <- full_steps_old(ordata_H14, 200, filter_none)

distance_data_walk1 <- full_groups(dataframes_walk1[[2]], sign_disagree)
distance_data_walk2 <- full_groups(dataframes_walk2[[2]], sign_disagree)
distance_data_walk3 <- full_groups(dataframes_walk3[[2]], sign_disagree)
distance_data_walk4 <- full_groups(dataframes_walk4[[2]], sign_disagree)
distance_data_walk5 <- full_groups(dataframes_walk5[[2]], sign_disagree)
distance_data_walk6 <- full_groups(dataframes_walk6[[2]], sign_disagree)
distance_data_walk7 <- full_groups(dataframes_walk7[[2]], sign_disagree)
distance_data_walk8 <- full_groups(dataframes_walk8[[2]], sign_disagree)
distance_data_walk9 <- full_groups(dataframes_walk9[[2]], sign_disagree)
distance_data_walk10 <- full_groups(dataframes_walk10[[2]], sign_disagree)
distance_data_walk2_low <- full_groups(dataframes_walk2_low[[2]], sign_disagree)
distance_data_walk3_low <- full_groups(dataframes_walk3_low[[2]], sign_disagree)
distance_data_walk4_low <- full_groups(dataframes_walk4_low[[2]], sign_disagree)
distance_data_walk5_low <- full_groups(dataframes_walk5_low[[2]], sign_disagree)
distance_data_H10 <- full_groups(dataframes_H10[[2]], sign_disagree)
distance_data_H11 <- full_groups(dataframes_H11[[2]], sign_disagree)
distance_data_H12 <- full_groups(dataframes_H12[[2]], sign_disagree)
distance_data_H13 <- full_groups(dataframes_H13[[2]], sign_disagree)
distance_data_H14 <- full_groups(dataframes_H14[[2]], sign_disagree)

distance_data_walk1_adp <- full_groups(dataframes_walk1[[2]], sumabsdiffpercentage)
distance_data_walk2_adp <- full_groups(dataframes_walk2[[2]], sumabsdiffpercentage)
distance_data_walk3_adp <- full_groups(dataframes_walk3[[2]], sumabsdiffpercentage)
distance_data_walk4_adp <- full_groups(dataframes_walk4[[2]], sumabsdiffpercentage)
distance_data_walk5_adp <- full_groups(dataframes_walk5[[2]], sumabsdiffpercentage)
distance_data_walk6_adp <- full_groups(dataframes_walk6[[2]], sumabsdiffpercentage)
distance_data_walk7_adp <- full_groups(dataframes_walk7[[2]], sumabsdiffpercentage)
distance_data_walk8_adp <- full_groups(dataframes_walk8[[2]], sumabsdiffpercentage)
distance_data_walk9_adp <- full_groups(dataframes_walk9[[2]], sumabsdiffpercentage)
distance_data_walk10_adp <- full_groups(dataframes_walk10[[2]], sumabsdiffpercentage)
distance_data_walk2_low_adp <- full_groups(dataframes_walk2_low[[2]], sumabsdiffpercentage)
distance_data_walk3_low_adp <- full_groups(dataframes_walk3_low[[2]], sumabsdiffpercentage)
distance_data_walk4_low_adp <- full_groups(dataframes_walk4_low[[2]], sumabsdiffpercentage)
distance_data_walk5_low_adp <- full_groups(dataframes_walk5_low[[2]], sumabsdiffpercentage)
distance_data_H10_adp <- full_groups(dataframes_H10[[2]], sumabsdiffpercentage)
distance_data_H11_adp <- full_groups(dataframes_H11[[2]], sumabsdiffpercentage)
distance_data_H12_adp <- full_groups(dataframes_H12[[2]], sumabsdiffpercentage)
distance_data_H13_adp <- full_groups(dataframes_H13[[2]], sumabsdiffpercentage)
distance_data_H14_adp <- full_groups(dataframes_H14[[2]], sumabsdiffpercentage)

distance_data_walk1_cos <- full_groups(dataframes_walk1[[2]], cosine_similarity)
distance_data_walk2_cos <- full_groups(dataframes_walk2[[2]], cosine_similarity)
distance_data_walk3_cos <- full_groups(dataframes_walk3[[2]], cosine_similarity)
distance_data_walk4_cos <- full_groups(dataframes_walk4[[2]], cosine_similarity)
distance_data_walk5_cos <- full_groups(dataframes_walk5[[2]], cosine_similarity)
distance_data_walk6_cos <- full_groups(dataframes_walk6[[2]], cosine_similarity)
distance_data_walk7_cos <- full_groups(dataframes_walk7[[2]], cosine_similarity)
distance_data_walk8_cos <- full_groups(dataframes_walk8[[2]], cosine_similarity)
distance_data_walk9_cos <- full_groups(dataframes_walk9[[2]], cosine_similarity)
distance_data_walk10_cos <- full_groups(dataframes_walk10[[2]], cosine_similarity)
distance_data_walk2_low_cos <- full_groups(dataframes_walk2_low[[2]], cosine_similarity)
distance_data_walk3_low_cos <- full_groups(dataframes_walk3_low[[2]], cosine_similarity)
distance_data_walk4_low_cos <- full_groups(dataframes_walk4_low[[2]], cosine_similarity)
distance_data_walk5_low_cos <- full_groups(dataframes_walk5_low[[2]], cosine_similarity)
distance_data_H10_cos <- full_groups(dataframes_H10[[2]], cosine_similarity)
distance_data_H11_cos <- full_groups(dataframes_H11[[2]], cosine_similarity)
distance_data_H12_cos <- full_groups(dataframes_H12[[2]], cosine_similarity)
distance_data_H13_cos <- full_groups(dataframes_H13[[2]], cosine_similarity)
distance_data_H14_cos <- full_groups(dataframes_H14[[2]], cosine_similarity)

distance_data_walk1_peak <- full_groups(dataframes_walk1[[2]], peak_height)
distance_data_walk2_peak <- full_groups(dataframes_walk2[[2]], peak_height)
distance_data_walk3_peak <- full_groups(dataframes_walk3[[2]], peak_height)
distance_data_walk4_peak <- full_groups(dataframes_walk4[[2]], peak_height)
distance_data_walk5_peak <- full_groups(dataframes_walk5[[2]], peak_height)
distance_data_walk6_peak <- full_groups(dataframes_walk6[[2]], peak_height)
distance_data_walk7_peak <- full_groups(dataframes_walk7[[2]], peak_height)
distance_data_walk8_peak <- full_groups(dataframes_walk8[[2]], peak_height)
distance_data_walk9_peak <- full_groups(dataframes_walk9[[2]], peak_height)
distance_data_walk10_peak <- full_groups(dataframes_walk10[[2]], peak_height)
distance_data_walk2_low_peak <- full_groups(dataframes_walk2_low[[2]], peak_height)
distance_data_walk3_low_peak <- full_groups(dataframes_walk3_low[[2]], peak_height)
distance_data_walk4_low_peak <- full_groups(dataframes_walk4_low[[2]], peak_height)
distance_data_walk5_low_peak <- full_groups(dataframes_walk5_low[[2]], peak_height)

distance_data_walk1_rsadsquare <- full_groups(dataframes_walk1[[2]], rescaled_sumsquared)
distance_data_walk2_rsadsquare <- full_groups(dataframes_walk2[[2]], rescaled_sumsquared)
distance_data_walk3_rsadsquare <- full_groups(dataframes_walk3[[2]], rescaled_sumsquared)
distance_data_walk4_rsadsquare <- full_groups(dataframes_walk4[[2]], rescaled_sumsquared)
distance_data_walk5_rsadsquare <- full_groups(dataframes_walk5[[2]], rescaled_sumsquared)
distance_data_walk6_rsadsquare <- full_groups(dataframes_walk6[[2]], rescaled_sumsquared)
distance_data_walk7_rsadsquare <- full_groups(dataframes_walk7[[2]], rescaled_sumsquared)
distance_data_walk8_rsadsquare <- full_groups(dataframes_walk8[[2]], rescaled_sumsquared)
distance_data_walk9_rsadsquare <- full_groups(dataframes_walk9[[2]], rescaled_sumsquared)
distance_data_walk10_rsadsquare <- full_groups(dataframes_walk10[[2]], rescaled_sumsquared)
distance_data_walk2_low_rsadsquare <- full_groups(dataframes_walk2_low[[2]], rescaled_sumsquared)
distance_data_walk3_low_rsadsquare <- full_groups(dataframes_walk3_low[[2]], rescaled_sumsquared)
distance_data_walk4_low_rsadsquare <- full_groups(dataframes_walk4_low[[2]], rescaled_sumsquared)
distance_data_walk5_low_rsadsquare <- full_groups(dataframes_walk5_low[[2]], rescaled_sumsquared)

distance_data_walk1_cor <- full_groups(dataframes_walk1[[2]], correlation_distance)
distance_data_walk2_cor <- full_groups(dataframes_walk2[[2]], correlation_distance)
distance_data_walk3_cor <- full_groups(dataframes_walk3[[2]], correlation_distance)
distance_data_walk4_cor <- full_groups(dataframes_walk4[[2]], correlation_distance)
distance_data_walk5_cor <- full_groups(dataframes_walk5[[2]], correlation_distance)
distance_data_walk6_cor <- full_groups(dataframes_walk6[[2]], correlation_distance)
distance_data_walk7_cor <- full_groups(dataframes_walk7[[2]], correlation_distance)
distance_data_walk8_cor <- full_groups(dataframes_walk8[[2]], correlation_distance)
distance_data_walk9_cor <- full_groups(dataframes_walk9[[2]], correlation_distance)
distance_data_walk10_cor <- full_groups(dataframes_walk10[[2]], correlation_distance)
distance_data_walk2_low_cor <- full_groups(dataframes_walk2_low[[2]], correlation_distance)
distance_data_walk3_low_cor <- full_groups(dataframes_walk3_low[[2]], correlation_distance)
distance_data_walk4_low_cor <- full_groups(dataframes_walk4_low[[2]], correlation_distance)
distance_data_walk5_low_cor <- full_groups(dataframes_walk5_low[[2]], correlation_distance)
distance_data_H10_cor <- full_groups(dataframes_H10[[2]], correlation_distance)
distance_data_H11_cor <- full_groups(dataframes_H11[[2]], correlation_distance)
distance_data_H12_cor <- full_groups(dataframes_H12[[2]], correlation_distance)
distance_data_H13_cor <- full_groups(dataframes_H13[[2]], correlation_distance)
distance_data_H14_cor <- full_groups(dataframes_H14[[2]], correlation_distance)

distance_data_walk1_rsad <- full_groups(dataframes_walk1[[2]], rescaled_sumabsdiff)
distance_data_walk2_rsad <- full_groups(dataframes_walk2[[2]], rescaled_sumabsdiff)
distance_data_walk3_rsad <- full_groups(dataframes_walk3[[2]], rescaled_sumabsdiff)
distance_data_walk4_rsad <- full_groups(dataframes_walk4[[2]], rescaled_sumabsdiff)
distance_data_walk5_rsad <- full_groups(dataframes_walk5[[2]], rescaled_sumabsdiff)
distance_data_walk6_rsad <- full_groups(dataframes_walk6[[2]], rescaled_sumabsdiff)
distance_data_walk7_rsad <- full_groups(dataframes_walk7[[2]], rescaled_sumabsdiff)
distance_data_walk8_rsad <- full_groups(dataframes_walk8[[2]], rescaled_sumabsdiff)
distance_data_walk9_rsad <- full_groups(dataframes_walk9[[2]], rescaled_sumabsdiff)
distance_data_walk10_rsad <- full_groups(dataframes_walk10[[2]], rescaled_sumabsdiff)
```


## Approach 1: fixed parameters, try a few values
We use normal DBSCAN with a few fixed parameter values. The distance function should support this and be independent of specifics of the individuals / rescaled in some sense.

```{r}
#Generate all pictures of the adp with same parameters
D <- distance_data_H10_adp[[1]]
D <- distance_data_walk1_adp[[1]]
D <- distance_data_walk5_low_adp[[1]]
D <- distance_data_walk5_low_cos[[1]]
density <- 185
points <- 3
density <- 0.22
points <- 3

(noise_frac <- sum(dbscan(as.dist(D), density, points)$clust == 0)/nrow(D)) #The 5 should maybe scale with total number of steps somewhat? Or just make it 3 and probably do not scale at all, any movement should have at least 3 steps practically. Or even make it 2 in this case. Just try a few

clustering <- dbscan(as.dist(D), density, points)$clust

#Visualise through MDS
mds_result <- cmdscale(as.dist(D), k = 3, eig = T)
coords <- as.data.frame(mds_result$points)
colnames(coords) <- c("X", "Y", "Z")

coords$cluster <- as.factor(clustering)

plot_ly(coords, x = ~X, y = ~Y, z = ~Z, color = ~cluster,
        type = 'scatter3d', mode = 'markers',
        marker = list(size = 4))
```

We now load the results we get into a table to visualise in different ways + compare with other data from the individuals

```{r}
numbers <- c(1:19)
names <- c("Rocco", "Pleun", "Estelle", "Emma", "Elvira", "Sverre", "Devin", "Gerwin", "Roel", "Mike", "H10", "H11", "H12", "H13", "H14", "PleunLow", "EstelleLow", "EmmaLow", "ElviraLow")
df_walks <- data.frame(numbers = numbers, names = names)
df_walks$age <- c(16, 11, 15.75, 12.17, 12.08, 10.33, 8.83, 9.92, 19, 10.5, 9.5, NA, NA, NA, NA, 11, 15.75, 12.17, 12.08) 
df_walks$distance_approx <- c(570, 400, 180, 300, 220, 650, 450, 420, 440, 560, NA, NA, NA, NA, NA, 400, 180, 300, 220) #Approx until actually back
#And here sth with walking quality
  
no_steps <- c()
noise_frac_sgn <- c()
noise_frac_adp <- c()
noise_frac_cos <- c()
noise_frac_cor <- c()
for(j in 1:10){
  no_steps <- append(no_steps, get(paste0("dataframes_walk", j))[[1]] %>% nrow())
  D <- get(paste0("distance_data_walk", j))[[1]]
  noise_frac_sgn <- append(noise_frac_sgn, sum(dbscan(as.dist(D), 30, 3)$clust == 0)/nrow(D))
  D <- get(paste0("distance_data_walk", j, "_adp"))[[1]]
  noise_frac_adp <- append(noise_frac_adp, sum(dbscan(as.dist(D), 180, 3)$clust == 0)/nrow(D))
  # D <- get(paste0("distance_data_walk", j, "_cos"))[[1]]
  # noise_frac_cos <- append(noise_frac_cos, sum(dbscan(as.dist(D), 180, 3)$clust == 0)/nrow(D))
  D <- get(paste0("distance_data_walk", j, "_cor"))[[1]]
  noise_frac_cos <- append(noise_frac_cos, sum(dbscan(as.dist(D), 0.22, 3)$clust == 0)/nrow(D))
}
no_steps <- append(no_steps, c(nrow(dataframes_H10[[1]]), 
                   nrow(dataframes_H11[[1]]),
                   nrow(dataframes_H12[[1]]),
                   nrow(dataframes_H13[[1]]),
                   nrow(dataframes_H14[[1]]),
                   nrow(dataframes_walk2_low[[1]]),
                   nrow(dataframes_walk3_low[[1]]),
                   nrow(dataframes_walk4_low[[1]]),
                   nrow(dataframes_walk5_low[[1]]))
                   )
D <- distance_data_H10[[1]]
noise_frac_sgn <- append(noise_frac_sgn, sum(dbscan(as.dist(D), 30, 3)$clust == 0)/nrow(D))
D <- distance_data_H10_adp[[1]]
noise_frac_adp <- append(noise_frac_adp, sum(dbscan(as.dist(D), 180, 3)$clust == 0)/nrow(D))
D <- distance_data_H10_cos[[1]]
noise_frac_cos <- append(noise_frac_cos, sum(dbscan(as.dist(D), 0.22, 3)$clust == 0)/nrow(D))
D <- distance_data_H11[[1]]
noise_frac_sgn <- append(noise_frac_sgn, sum(dbscan(as.dist(D), 30, 3)$clust == 0)/nrow(D))
D <- distance_data_H11_adp[[1]]
noise_frac_adp <- append(noise_frac_adp, sum(dbscan(as.dist(D), 180, 3)$clust == 0)/nrow(D))
D <- distance_data_H11_cos[[1]]
noise_frac_cos <- append(noise_frac_cos, sum(dbscan(as.dist(D), 0.22, 3)$clust == 0)/nrow(D))
D <- distance_data_H12[[1]]
noise_frac_sgn <- append(noise_frac_sgn, sum(dbscan(as.dist(D), 30, 3)$clust == 0)/nrow(D))
D <- distance_data_H12_adp[[1]]
noise_frac_adp <- append(noise_frac_adp, sum(dbscan(as.dist(D), 180, 3)$clust == 0)/nrow(D))
D <- distance_data_H12_cos[[1]]
noise_frac_cos <- append(noise_frac_cos, sum(dbscan(as.dist(D), 0.22, 3)$clust == 0)/nrow(D))
D <- distance_data_H13[[1]]
noise_frac_sgn <- append(noise_frac_sgn, sum(dbscan(as.dist(D), 30, 3)$clust == 0)/nrow(D))
D <- distance_data_H13_adp[[1]]
noise_frac_adp <- append(noise_frac_adp, sum(dbscan(as.dist(D), 180, 3)$clust == 0)/nrow(D))
D <- distance_data_H13_cos[[1]]
noise_frac_cos <- append(noise_frac_cos, sum(dbscan(as.dist(D), 0.22, 3)$clust == 0)/nrow(D))
D <- distance_data_H14[[1]]
noise_frac_sgn <- append(noise_frac_sgn, sum(dbscan(as.dist(D), 30, 3)$clust == 0)/nrow(D))
D <- distance_data_H14_adp[[1]]
noise_frac_adp <- append(noise_frac_adp, sum(dbscan(as.dist(D), 180, 3)$clust == 0)/nrow(D))
D <- distance_data_H14_cos[[1]]
noise_frac_cos <- append(noise_frac_cos, sum(dbscan(as.dist(D), 0.22, 3)$clust == 0)/nrow(D))
D <- distance_data_walk2_low[[1]]
noise_frac_sgn <- append(noise_frac_sgn, sum(dbscan(as.dist(D), 30, 3)$clust == 0)/nrow(D))
D <- distance_data_walk2_low_adp[[1]]
noise_frac_adp <- append(noise_frac_adp, sum(dbscan(as.dist(D), 180, 3)$clust == 0)/nrow(D))
D <- distance_data_walk2_low_cos[[1]]
noise_frac_cos <- append(noise_frac_cos, sum(dbscan(as.dist(D), 0.22, 3)$clust == 0)/nrow(D))
D <- distance_data_walk3_low[[1]]
noise_frac_sgn <- append(noise_frac_sgn, sum(dbscan(as.dist(D), 30, 3)$clust == 0)/nrow(D))
D <- distance_data_walk3_low_adp[[1]]
noise_frac_adp <- append(noise_frac_adp, sum(dbscan(as.dist(D), 180, 3)$clust == 0)/nrow(D))
D <- distance_data_walk3_low_cos[[1]]
noise_frac_cos <- append(noise_frac_cos, sum(dbscan(as.dist(D), 0.22, 3)$clust == 0)/nrow(D))
D <- distance_data_walk4_low[[1]]
noise_frac_sgn <- append(noise_frac_sgn, sum(dbscan(as.dist(D), 30, 3)$clust == 0)/nrow(D))
D <- distance_data_walk4_low_adp[[1]]
noise_frac_adp <- append(noise_frac_adp, sum(dbscan(as.dist(D), 180, 3)$clust == 0)/nrow(D))
D <- distance_data_walk4_low_cos[[1]]
noise_frac_cos <- append(noise_frac_cos, sum(dbscan(as.dist(D), 0.22, 3)$clust == 0)/nrow(D))
D <- distance_data_walk5_low[[1]]
noise_frac_sgn <- append(noise_frac_sgn, sum(dbscan(as.dist(D), 30, 3)$clust == 0)/nrow(D))
D <- distance_data_walk5_low_adp[[1]]
noise_frac_adp <- append(noise_frac_adp, sum(dbscan(as.dist(D), 180, 3)$clust == 0)/nrow(D))
D <- distance_data_walk5_low_cos[[1]]
noise_frac_cos <- append(noise_frac_cos, sum(dbscan(as.dist(D), 0.22, 3)$clust == 0)/nrow(D))

df_walks$no_steps <- no_steps
df_walks$noise_frac_sgn <- noise_frac_sgn
df_walks$noise_frac_adp <- noise_frac_adp
df_walks$noise_frac_cos <- noise_frac_cos

df_walks %>% view()
```

## Approach 2: multidimensional scaling + persistable
We use the most persistent parameters to get clusters for DBSCAN and take the corresponding noise size.

```{r}

```

... and add this to the table ...


# Below is all trying things out

## Investigation into which steps represent whole groups

```{r}
representative_list <- c()
group_fraction <- seq(0.02, 1, 0.02)

for(fraction in group_fraction){
  val_list <- c()
  for(j in 1:nrow(distance_data[[1]])){
    val <- quantile(unlist(distance_data[[1]][j,]), fraction)
    val_list <- append(val_list, val)
  }
  representative_list <- append(representative_list, which.min(val_list))
}
plot(representative_list, type = 'l')

```

## More classical clustering approach 1 - first is hierarchical clustering

```{r}
hc <- hclust(as.dist(distance_data[[1]]), method = "average")
plot(hc, labels = FALSE, hang = -1, main = "Hierarchical Clustering Dendrogram")

clusters <- cutree(hc, k = 5)
```

## Classical 2 - k-medoids (PAM)

```{r}
library(cluster)
pam_result <- pam(as.dist(distance_data[[1]]), k = 5)
clusters <- pam_result$clustering
```

## Classical 3 - classical multidimensional scaling // visualisation of all methods
```{r}
mds_result <- cmdscale(as.dist(distance_data[[1]]), k = 3, eig = T)
#What does the k = 3 do in cmdscale: best fitting 3-dimensional representation of the steps!
coords <- as.data.frame(mds_result$points)
colnames(coords) <- c("X", "Y", "Z")

library(plotly)

coords$cluster <- as.factor(clusters)

plot_ly(coords, x = ~X, y = ~Y, z = ~Z, color = ~cluster,
        type = 'scatter3d', mode = 'markers',
        marker = list(size = 4)) %>%
  layout(title = '3D MDS with Clusters')

# plot_ly(coords, x = ~X, y = ~Y, z = ~Z,
#         type = 'scatter3d', mode = 'markers',
#         marker = list(size = 3, color = 'blue')) %>%
#   layout(title = '3D MDS Projection',
#          scene = list(xaxis = list(title = 'X'),
#                       yaxis = list(title = 'Y'),
#                       zaxis = list(title = 'Z')))
```

## Classical 4 - clustering using DBSCAN

```{r}
D <- distance_data[[1]]
coords <- cmdscale(as.dist(D), k = 178, eig = T)$points

sum((as.matrix(dist(coords)) - D)^2) / sum(D^2)

strain <- sum((dist(coords) - as.dist(D))^2) / sum(D^2)

dbscan(as.dist(D), 90, 5)
```

Own ``Persistable variant'' in R (but no homology...):

```{r}
epsrange <- seq(0, max(D), max(D)/50)
stepfraction <- seq(0, 0.2, 0.01)
component_counter <- data.frame(matrix(nrow = length(epsrange), ncol = length(stepfraction)))
noise_size_counter <- data.frame(matrix(nrow = length(epsrange), ncol = length(stepfraction)))

for(i in 1:length(epsrange)){
  for(j in 1:length(stepfraction)){
    db_result <- dbscan(as.dist(D), epsrange[i], floor(nrow(D)*stepfraction[j]))
    component_counter[i,j] <- length(unique(db_result$cluster))
    noise_size_counter[i,j] <- sum(db_result$cluster == 0)
  }
}

component_long <- as.data.frame(as.table(as.matrix(component_counter)))
noise_long <- as.data.frame(as.table(as.matrix(noise_size_counter + 1)))

ggplot(component_long, aes(x = Var1, y = Var2, fill = Freq)) +
  geom_tile() +
  scale_fill_gradient(
    trans = "log10",
    low = "white",
    high = "black"
  ) +
  theme_minimal() +
  coord_fixed()

```

```{r}
db <- dbscan(coords, eps = 100, minPts = 5)
hdb <- hdbscan(coords, minPts = 3)
library(plotly)
coords3d <- as.data.frame(cmdscale(as.dist(distance_data[[1]]), k = 3))
coords3d$cluster <- as.factor(hdb$cluster)

plot_ly(coords3d, x = ~V1, y = ~V2, z = ~V3, color = ~cluster,
        type = 'scatter3d', mode = 'markers',
        marker = list(size = 4)) %>%
  layout(title = '3D MDS with Clusters')
```

Now through Python: getting step data into Python to apply Persistable and DBSCAN*

```{r}

```

## Classical 5 - clustering using HDBSCAN

```{r}

```

## Classical 6 - topological data analysis technique with vineyards (?!?!)

```{r}

```


## Attempt 7 - My own method of taking out steps one by one and then 