### Importing libraries
We first important the libraries we need.

```{r, message=F, warning=F}
#Data analysis
library(tidyverse)
library(GGally)
library(patchwork)
library(scales)
library(RColorBrewer)

#Working with the activity class and data files
library(lubridate)
library(read.gt3x)
library(PhysicalActivity)

#Solving equations
library(nleqslv)
library(pracma)
library(MASS)
```

```{r}
df <- df_excl_walk
df$weight <- c(40.4, 54, 34, 40.4, 29.5, 35.4, 27.2, 53.1, 34, 27.2, 30.8, 20.9, 34.9, 24.9, 34.9, 30.4, 20.4, 78.4, 29.5, 82.5, 80.0)
df$height <- c(160, 160, 137.2, 142.2, 134.6, 147.3, 134.6, 154.9, 134.6, 132.1, 137.2, 119.4, 132.1, 124.5, 137.2, 142.2, 116.8, 132.1, 152.4, 202, 184)

#Change if run in different order: differences_length_all not usable with mean_alt, extreme_frac because mean that is taken will be 0
# df <- select (... 38, 39, 53, 54 run from high to low)
which((apply(df[, 5:204], 2, var) < 1e-12))
df2 <- df[, -c(23, 24, 68, 69)]

#Colinearity due to the functions doing the same
df2[,7] - df2[,8]
df2[,36] - df2[, 37]
df2[, 51] - df2[, 52]
# df2 <- df2[, -c(8, 37, 52)]
```

First we put in all the step functions with all parameters we want.

```{r}
data_functions_step_small <- list( list("fw_relative", 0), 
                             list("vert_relative", 0),
                             list("side_relative", 0),
                             list("fw_max", 0),
                             list("vert_max", 0),
                             list("side_max", 0),
                             list("val_v_peak", 0),
                             list("explosive_fw", 0),
                             list("explosive_vert", 0),
                             list("explosive_side", 0),
                             list("fw_variance", 0),
                             list("side_variance", 0),
                             list("vert_variance", 0),
                             list("sign_changes_fw", 0),
                             list("sign_changes_vert", 0),
                             list("sign_changes_side", 0),
                             list("cor_fw_cyclic_normalised", 0.5),
                             list("cor_vert_cyclic_normalised", 0.5),
                             list("cor_side_cyclic_normalised", 0.5),
                             list("cor_fw_vert_cyclic_normalised", 0.25),
                             list("cor_fw_vert_cyclic_normalised", 0.5),
                             list("cor_fw_vert_cyclic_normalised", 0.75),
                             list("cor_vert_side_cyclic_normalised", 0.25),
                             list("cor_vert_side_cyclic_normalised", 0.5),
                             list("cor_vert_side_cyclic_normalised", 0.75)
                             ) 


data_functions_step <- list( list("fw_relative", 0), 
                             list("vert_relative", 0),
                             list("side_relative", 0),
                             list("fw_absolute", 0),
                             list("vert_absolute", 0),
                             list("side_absolute", 0),
                             list("fw_max", 0),
                             list("vert_max", 0),
                             list("side_max", 0),
                             list("val_v_peak", 0),
                             list("explosive_fw", 0),
                             list("explosive_vert", 0),
                             list("explosive_side", 0),
                             list("fw_variance", 0),
                             list("side_variance", 0),
                             list("vert_variance", 0),
                             list("sign_changes_fw", 0),
                             list("sign_changes_vert", 0),
                             list("sign_changes_side", 0),
                             list("cor_fw_cyclic_normalised", 0.1),
                             list("cor_fw_cyclic_normalised", 0.3),
                             list("cor_fw_cyclic_normalised", 0.5),
                             list("cor_fw_cyclic_normalised", 0.7),
                             list("cor_fw_cyclic_normalised", 0.9),
                             list("cor_vert_cyclic_normalised", 0.1),
                             list("cor_vert_cyclic_normalised", 0.3),
                             list("cor_vert_cyclic_normalised", 0.5),
                             list("cor_vert_cyclic_normalised", 0.7),
                             list("cor_vert_cyclic_normalised", 0.9),
                             list("cor_side_cyclic_normalised", 0.1),
                             list("cor_side_cyclic_normalised", 0.3),
                             list("cor_side_cyclic_normalised", 0.5),
                             list("cor_side_cyclic_normalised", 0.7),
                             list("cor_side_cyclic_normalised", 0.9),
                             list("cor_fw_side_cyclic_normalised", 0.1),
                             list("cor_fw_side_cyclic_normalised", 0.3),
                             list("cor_fw_side_cyclic_normalised", 0.5),
                             list("cor_fw_side_cyclic_normalised", 0.7),
                             list("cor_fw_side_cyclic_normalised", 0.9),
                             list("cor_fw_vert_cyclic_normalised", 0.1),
                             list("cor_fw_vert_cyclic_normalised", 0.3),
                             list("cor_fw_vert_cyclic_normalised", 0.5),
                             list("cor_fw_vert_cyclic_normalised", 0.7),
                             list("cor_fw_vert_cyclic_normalised", 0.9),
                             list("cor_vert_side_cyclic_normalised", 0.1),
                             list("cor_vert_side_cyclic_normalised", 0.3),
                             list("cor_vert_side_cyclic_normalised", 0.5),
                             list("cor_vert_side_cyclic_normalised", 0.7),
                             list("cor_vert_side_cyclic_normalised", 0.9)
                             ) 

```

```{r}
data_functions_test <- list( list("fw_relative", 0), 
                             list("vert_relative", 0))
```

Now we want this for general metric functions and filter functions.

```{r}
filter_metric_functions_step_small <- list(list("freq_selector", c(14, 21), "quantile_bottom", 0.5),
                                     list("freq_selector", c(14, 21), "mean_alt", 0),
                                     list("freq_selector", c(14, 21), "var_alt", 0),
                                     list("freq_selector", c(14, 21), "trimmed_mean", 0.2),
                                     list("freq_selector", c(14, 21), "extreme_frac", c(1.5, 0.75))
                                     )

filter_metric_functions_step <- list(list("freq_selector", c(14, 21), "quantile_bottom", 0.2),
                                     list("freq_selector", c(14, 21), "quantile_bottom", 0.5),
                                     list("freq_selector", c(14, 21), "quantile_bottom", 0.8),
                                     list("freq_selector", c(14, 21), "mean_alt", 0),
                                     list("freq_selector", c(14, 21), "var_alt", 0),
                                     list("freq_selector", c(14, 21), "trimmed_mean", 0.1),
                                     list("freq_selector", c(14, 21), "trimmed_mean", 0.3),
                                     list("freq_selector", c(14, 21), "extreme_frac", c(1.5, 0)),
                                     list("freq_selector", c(14, 21), "extreme_frac", c(0, 0.75)),
                                     list("freq_selector", c(16, 19), "quantile_bottom", 0.2),
                                     list("freq_selector", c(16, 19), "quantile_bottom", 0.5),
                                     list("freq_selector", c(16, 19), "quantile_bottom", 0.8),
                                     list("freq_selector", c(16, 19), "mean_alt", 0),
                                     list("freq_selector", c(16, 19), "var_alt", 0),
                                     list("freq_selector", c(16, 19), "trimmed_mean", 0.1),
                                     list("freq_selector", c(16, 19), "trimmed_mean", 0.3),
                                     list("freq_selector", c(16, 19), "extreme_frac", c(0, 0.75)),
                                     list("freq_selector", c(16, 19), "extreme_frac", c(1.5, 0)),
                                     list("default", 0, "quantile_bottom", 0.2),
                                     list("default", 0, "quantile_bottom", 0.5),
                                     list("default", 0, "quantile_bottom", 0.8),
                                     list("default", 0, "mean_alt", 0),
                                     list("default", 0, "var_alt", 0),
                                     list("default", 0, "trimmed_mean", 0.1),
                                     list("default", 0, "trimmed_mean", 0.3),
                                     list("default", 0, "extreme_frac", c(0, 0.75)),
                                     list("default", 0, "extreme_frac", c(1.5, 0))
                                     )
```

```{r}
filter_metric_functions <- filter_metric_functions_step_small
data_functions <- data_functions_step_small

j <- 0
total <- length(filter_metric_functions) * length(data_functions)

for(info in filter_metric_functions){
  for(data_func in data_functions){
    df <- add_step_metric_idv(df, 
                              paste0(data_func[[1]], paste(data_func[[2]], collapse = "-"), "_", info[[1]], paste(info[[2]], collapse = "-"), "_", info[[3]], paste(info[[4]], collapse = "-")), 
                              get(info[[1]]), 
                              info[[2]], 
                              get(data_func[[1]]), 
                              data_func[[2]], 
                              get(info[[3]]), 
                              info[[4]])
    j <- j + 1
    print(paste0("Progress: ", j/total))
  }
}
```

We now continue manipulating the dataframe by doing the same for sequence functions instead of step functions:

```{r}
data_functions_seq_small <- list(list("correlations_at_lag_var", 0),
                                 list("variance_length_all", T),
                                 list("variance_length_all", F),
                                 list("differences_length_all", T),
                                 list("differences_length_all", F),
                                 list("correlations_at_lag_mean", 0),
                                 list("kth_hill_fft_fw", c(60, 1)),
                                 list("kth_hill_fft_fw", c(60, 2)),
                                 list("kth_hill_fft_fw", c(60, 3)),
                                 list("kth_hill_fft_vert", c(60, 1)),
                                 list("kth_hill_fft_vert", c(60, 2)),
                                 list("kth_hill_fft_vert", c(60, 3)),
                                 list("kth_hill_fft_side", c(60, 1)),
                                 list("kth_hill_fft_side", c(60, 2)),
                                 list("kth_hill_fft_side", c(60, 3))
                                 )
```

```{r}
filter_metric_functions <- filter_metric_functions_step_small
data_functions <- data_functions_seq_small

j <- 0
total <- length(filter_metric_functions) * length(data_functions)

for(info in filter_metric_functions){
  for(data_func in data_functions){
    df <- add_seq_metric_idv(df, 
                              paste0(data_func[[1]], paste(data_func[[2]], collapse = "-"), "_", info[[1]], paste(info[[2]], collapse = "-"), "_", info[[3]], paste(info[[4]], collapse = "-")), 
                              get(info[[1]]), 
                              info[[2]], 
                              get(data_func[[1]]), 
                              data_func[[2]], 
                              get(info[[3]]), 
                              info[[4]])
    j <- j + 1
    print(paste0("Progress: ", j/total))
  }
}
```

## Analysis

First we run a normal PCA, purely to see which components contain most information.

```{r}
df2$type <- ifelse(df$type == "S", 1, 0)
view(df2)
# df2 <- df2[-3]

pca_result <- prcomp(df2[, 2:198], scale. = TRUE) #Includes 4, age and 201, 202, weight and length
summary(pca_result) 
pca_scores <- as.data.frame(pca_result$x)
pca_scores$type <- df2$type
pca_scores$weight <- df2$weight
pca_scores$height <- df2$height
pca_scores$age <- df2$adjusted_age
pca_scores$feature_ex <- df2$`fw_max0_freq_selector14-21_quantile_bottom0.5`
pca_scores$feature_ex2 <- df2$`kth_hill_fft_fw60-3_freq_selector14-21_mean_alt0`

ggplot(pca_scores, aes(x = PC1, y = PC2, color = type, label = rownames(df))) +
  geom_point(size = 3) +
  geom_text(vjust = 1.5, size = 3) +  # Add labels
  theme_minimal() +
  labs(title = "PCA: First Two Principal Components", x = "PC1", y = "PC2")

ggplot(pca_scores, aes(x = PC1, y = PC2, color = height)) +
  geom_point(size = 3) +
  scale_color_gradient(low = "blue", high = "red") +  # Adjust color gradient
  theme_minimal() +
  labs(title = "PCA: First Two Principal Components", x = "PC1", y = "PC2", color = "length")

ggplot(pca_scores, aes(x = PC1, y = PC2, color = `feature_ex2`)) +
  geom_point(size = 3) +
  scale_color_gradient(low = "blue", high = "red") +  # Adjust color gradient
  theme_minimal() +
  labs(title = "PCA: First Two Principal Components", x = "PC1", y = "PC2", color = "mean frac frequency located in main hill")

ggplot(pca_scores, aes(x = PC1, y = PC2, color = feature_ex)) +
  geom_point(size = 3) +
  scale_color_gradient(low = "blue", high = "red") +  # Adjust color gradient
  theme_minimal() +
  labs(title = "PCA: First Two Principal Components", x = "PC1", y = "PC2", color = "median absolute fw acc")



loadings <- pca_result$rotation
pc1_contributions <- loadings[, 1]
pc2_contributions <- loadings[, 2]
pc3_contributions <- loadings[, 2]
top_features_pc1 <- sort(abs(pc1_contributions), decreasing = TRUE)
top_features_pc1_names <- names(top_features_pc1)
top_features_pc2 <- sort(abs(pc2_contributions), decreasing = TRUE)
top_features_pc2_names <- names(top_features_pc2)
top_features_pc3 <- sort(abs(pc3_contributions), decreasing = TRUE)
top_features_pc3_names <- names(top_features_pc3)
top_features_pc1[1:10] 
top_features_pc2[1:10] 
top_features_pc3[1:10] 
```

Now we turn to more interesting questions: 

```{r}
cor_matrix <- cor(df2[, 4:196], use = "complete.obs")
high_correlations <- which(abs(cor_matrix) > 0.99999, arr.ind = TRUE)
print(high_correlations)

lda_result <- lda(type ~ ., data = df2[, c(2, 4:196)], subset = type %in% c(0, 1))
top_features_lda <- names(sort(abs(lda_result$scaling[, 1]), decreasing = TRUE)[1:5])
print(top_features_lda)

ggplot(df, aes(x = `kth_hill_fft_fw60-2_freq_selector14-21_var_alt0`, y = `correlations_at_lag_var0_freq_selector14-21_var_alt0`, color = type)) +
  geom_point() +
  theme_minimal()
```

Now find within both groups features that correlate well weight age, length, weight
```{r}
df3 <- df2[1:19,]

correlation_scores <- df3 %>%
  filter(type %in% c(0, 1)) %>%
  group_by(type) %>%
  summarise(across(4:196, ~ cor(.x, adjusted_age, use = "pairwise.complete.obs"), .names = "cor_age_{.col}"),
            across(4:196, ~ cor(.x, height, use = "pairwise.complete.obs"), .names = "cor_length_{.col}"),
            across(4:196, ~ cor(.x, weight, use = "pairwise.complete.obs"), .names = "cor_weight_{.col}"))

scores <- correlation_scores[, 2:580]

for(j in 194:386){
  if(scores[1, j] * scores[2, j] > 0.5){
    print(j)
  }
}

for(j in 194:386){
  if(scores[1, j] * scores[2, j] > 0.25 & scores[2,j - 193] > 0.25){
    print(j)
  }
}

scores[, 203]
scores[, 216]
scores[, 219]
scores[, 244]
scores[, 377]
scores[, 237]
```

```{r}
ggplot(df3, aes(x = `kth_hill_fft_side60-3_freq_selector14-21_mean_alt0`, y = `height`, color = type)) +
  geom_point() +
  theme_minimal()

ggplot(df3, aes(x = `differences_length_allTRUE_freq_selector14-21_trimmed_mean0.2`, y = `height`, color = type)) +
  geom_point() +
  theme_minimal()
```