### Importing libraries
We first important the libraries we need.

```{r, message=F, warning=F}
#Data analysis
library(tidyverse)
library(patchwork)
library(scales)
library(RColorBrewer)

#Working with the activity class and data files
library(lubridate)
library(read.gt3x)
library(PhysicalActivity)

#Solving equations
library(nleqslv)
library(pracma)
library(latex2exp)

#Reshaping / data manipulation
library(reshape2)
library(data.table)
```

Playing around with some steps, trying to see which metrics make sense

```{r}
seq_A20_1[[1]]$data %>% filter(in_step_bw == 1) %>% pull(acc_fw) %>% plot(type = 'l')
seq_A20_1[[3]]$data %>% filter(in_step_fw == 2) %>% pull(acc_fw) %>% plot(type = 'l')

seq_H10_2[[252]]$data %>% filter(in_step_bw == 1) %>% pull(acc_vert) %>% plot(type = 'l')
seq_H10_2[[252]]$data %>% filter(in_step_fw == 1) %>% pull(acc_vert) %>% plot(type = 'l')

seq_H12_2[[332]]$data %>% filter(in_step_bw == 1) %>% pull(acc_vert) %>% plot(type = 'l')
seq_H12_2[[332]]$data %>% filter(in_step_bw == 2) %>% pull(acc_vert) %>% plot(type = 'l')

#Finding some nice normal walking (?) to compare

valid_idc <- c()
for(j in 1:500){
  if(seq_H12_2[[j]]$main_freq > 15 &
     seq_H12_2[[j]]$main_freq < 25 &
     seq_H12_2[[j]]$len > 300){
    valid_idc <- append(valid_idc, j)
  }
}

test_step <- filter(seq_A20_1[[1]]$data, in_step_fw == 1)
```

```{r}
fw_vert_side_A20 <- average_step(c(seq_A20_1, seq_A20_2, seq_A20_3, seq_A20_4, seq_A20_5, seq_A20_6, seq_A20_7, seq_A20_8, seq_A20_9), 
                                 200, freq_selector, c(14,21))
plot(fw_vert_side_A20[[1]], type = 'l')
# summ <- 0
# test_seq <- seq_A20_5
# for(j in 1:length(test_seq)){
#   if(test_seq[[j]]$movement_type == "Walk"){
#     summ <- summ + test_seq[[j]]$data %>% nrow()
#   }
# }
# summ
```

```{r}
fw_vert_side_A21 <- average_step(c(seq_A21_1, seq_A21_2, seq_A21_3, seq_A21_4, seq_A21_5, seq_A21_6), 
                                 200, freq_selector, c(14,21))
plot(fw_vert_side_A21[[1]], type = 'l')
```

```{r}
fw_vert_side_H10 <- average_step(c(seq_H10_1, seq_H10_2, seq_H10_3, seq_H10_4, seq_H10_5, seq_H10_7, seq_H10_8), 
                                 200, freq_selector, c(14,21))
plot(fw_vert_side_H10[[1]], type = 'l')
```

```{r}
for(element in c("S1", "S2", "S3", "S4", "S5", "S6", "S7", "S8", "S9", 
                 "H10", "H11", "H12", "H13", "H14", "H15", "H16", "H17", "H18", "H19",
                 "A20", "A21")){
  all <- list()
  for(item in get(paste0(element, "_list"))){
    all <- append(all, item)
    }
  
  assign(paste0("fw_vert_side_", element), average_step(all, 200, freq_selector, c(14,21)))
}

fw_vert_side_H17[[4]] #All except 17 min length of at least 1000 steps
```

We now do it again, but with the alternative method of averaging steps.

```{r}
for(element in c("S1", "S2", "S3", "S4", "S5", "S6", "S7", "S8", "S9", 
                 "H10", "H11", "H12", "H13", "H14", "H15", "H16", "H17", "H18", "H19",
                 "A20", "A21")){
  all <- list()
  for(item in get(paste0(element, "_list"))){
    all <- append(all, item)
  }
  
  assign(paste0("fw_vert_side_", element), average_step_from_mvm(all, 250, freq_selector, c(14,21)))
}
```

We now save all the images through a loop.

```{r}
for(element in c("S1", "S2", "S3", "S4", "S5", "S6", "S7", "S8", "S9", 
                 "H10", "H11", "H12", "H13", "H14", "H15", "H16", "H17", "H18", "H19",
                 "A20", "A21")){
  
  assign(paste0("temp_df_", element), data.frame(row = 1:length(get(paste0("fw_vert_side_", element))[[1]]), 
                                               fw = get(paste0("fw_vert_side_", element))[[1]],
                                               vert = get(paste0("fw_vert_side_", element))[[2]],
                                               side = get(paste0("fw_vert_side_", element))[[3]])
         )
  
  plot1 <- ggplot(get(paste0("temp_df_", element)), aes(x = row, y = fw)) + 
  geom_line(color = "#56B4E9", linewidth = 0.9) +
  labs(
    x = "Index",
    y = TeX(r'( Acceleration in $m/s^2$ )'),
    title = paste0("Temp: fw person ", element)) +
  theme_minimal() +
  theme(
    text = element_text(size = 14),      
    axis.title = element_text(size = 14),   
    axis.text = element_text(size = 14),      
    legend.text = element_text(size = 14),     
    legend.title = element_text(size = 14),
    panel.background = element_rect(fill = "white", color = NA),
    plot.background = element_rect(fill = "white", color = NA)
  )
  plot2 <- ggplot(get(paste0("temp_df_", element)), aes(x = row, y = vert)) + 
  geom_line(color = "#D62728", linewidth = 0.9) +
  labs(
    x = "Index",
    y = TeX(r'( Acceleration in $m/s^2$ )'),
    title = paste0("Temp: vert person ", element)) +
  theme_minimal() +
  theme(
    text = element_text(size = 14),      
    axis.title = element_text(size = 14),   
    axis.text = element_text(size = 14),      
    legend.text = element_text(size = 14),     
    legend.title = element_text(size = 14),
    panel.background = element_rect(fill = "white", color = NA),
    plot.background = element_rect(fill = "white", color = NA)
  )
  plot3 <- ggplot(get(paste0("temp_df_", element)), aes(x = row, y = side)) + 
  geom_line(color = "#FFCC33", linewidth = 0.9) +
  labs(
    x = "Index",
    y = TeX(r'( Acceleration in $m/s^2$ )'),
    title = paste0("Temp: side person ", element)) +
  theme_minimal() +
  theme(
    text = element_text(size = 14),      
    axis.title = element_text(size = 14),   
    axis.text = element_text(size = 14),      
    legend.text = element_text(size = 14),     
    legend.title = element_text(size = 14),
    panel.background = element_rect(fill = "white", color = NA),
    plot.background = element_rect(fill = "white", color = NA)
  )
    plot4 <- ggplot(get(paste0("temp_df_", element)), aes(x = row)) + 
  geom_line(aes(y = fw, color = "fw"), linewidth = 0.9) +
  geom_line(aes(y = vert, color = "vert"), linewidth = 0.9) +
  geom_line(aes(y = side, color = "side"), linewidth = 0.9) +
  labs(
    x = "Index",
    y = TeX(r'( Acceleration in $m/s^2$ )'),
    title = paste0("Temp: combined person ", element)) +
      scale_color_manual(
        name = "",
        values = c("fw" = "#56B4E9", "vert" = "#D62728", "side" = "#FFCC33")
        ) +
  theme_minimal() +
  theme(
    text = element_text(size = 14),      
    axis.title = element_text(size = 14),   
    axis.text = element_text(size = 14),      
    legend.text = element_text(size = 14),     
    legend.title = element_text(size = 14),
    panel.background = element_rect(fill = "white", color = NA),
    plot.background = element_rect(fill = "white", color = NA)
  )
  
  ggsave(paste0("avg_fw_", element,".png"), plot1, width = 10, height = 4, dpi = 600)
  ggsave(paste0("avg_vert_", element,".png"), plot2, width = 10, height = 4, dpi = 600)
  ggsave(paste0("avg_side_", element,".png"), plot3, width = 10, height = 4, dpi = 600)
  ggsave(paste0("avg_comb_", element,".png"), plot4, width = 10, height = 4, dpi = 600)
}
```

###Misc. data/figures

```{r}
fw_vert_side_silly1 <- average_step_from_mvm(list(seq_silly[[1]], seq_silly[[2]], seq_silly[[3]], seq_silly[[4]]), 250, default, 0)
fw_vert_side_silly5 <- average_step_from_mvm(list(seq_silly[[5]], seq_silly[[6]], seq_silly[[7]]), 250, default, 0)
fw_vert_side_silly6 <- average_step_from_mvm(list(seq_silly[[8]], seq_silly[[9]]), 250, default, 0)

#fw_vert_side_misc1_1 <- average_step_from_mvm(seq_misc1_1, 250, freq_selector, c(14,21))
#fw_vert_side_misc1_2 <- average_step_from_mvm(seq_misc1_2, 250, freq_selector, c(14,21))
fw_vert_side_misc2_1 <- average_step_from_mvm(seq_misc2_1, 250, freq_selector, c(14,21))
fw_vert_side_misc2_2 <- average_step_from_mvm(seq_misc2_2, 250, freq_selector, c(14,21))
```

```{r}
for(element in c("silly1", "silly5", "silly6", "misc2_1", "misc2_2")){
  
  assign(paste0("temp_df_", element), data.frame(row = 1:length(get(paste0("fw_vert_side_", element))[[1]]), 
                                               fw = get(paste0("fw_vert_side_", element))[[1]],
                                               vert = get(paste0("fw_vert_side_", element))[[2]],
                                               side = get(paste0("fw_vert_side_", element))[[3]])
         )
  
  plot1 <- ggplot(get(paste0("temp_df_", element)), aes(x = row, y = fw)) + 
  geom_line(color = "#56B4E9", linewidth = 0.9) +
  labs(
    x = "Index",
    y = TeX(r'( Acceleration in $m/s^2$ )'),
    title = paste0("Temp: fw person ", element)) +
  theme_minimal() +
  theme(
    text = element_text(size = 14),      
    axis.title = element_text(size = 14),   
    axis.text = element_text(size = 14),      
    legend.text = element_text(size = 14),     
    legend.title = element_text(size = 14),
    panel.background = element_rect(fill = "white", color = NA),
    plot.background = element_rect(fill = "white", color = NA)
  )
  plot2 <- ggplot(get(paste0("temp_df_", element)), aes(x = row, y = vert)) + 
  geom_line(color = "#D62728", linewidth = 0.9) +
  labs(
    x = "Index",
    y = TeX(r'( Acceleration in $m/s^2$ )'),
    title = paste0("Temp: vert person ", element)) +
  theme_minimal() +
  theme(
    text = element_text(size = 14),      
    axis.title = element_text(size = 14),   
    axis.text = element_text(size = 14),      
    legend.text = element_text(size = 14),     
    legend.title = element_text(size = 14),
    panel.background = element_rect(fill = "white", color = NA),
    plot.background = element_rect(fill = "white", color = NA)
  )
  plot3 <- ggplot(get(paste0("temp_df_", element)), aes(x = row, y = side)) + 
  geom_line(color = "#FFCC33", linewidth = 0.9) +
  labs(
    x = "Index",
    y = TeX(r'( Acceleration in $m/s^2$ )'),
    title = paste0("Temp: side person ", element)) +
  theme_minimal() +
  theme(
    text = element_text(size = 14),      
    axis.title = element_text(size = 14),   
    axis.text = element_text(size = 14),      
    legend.text = element_text(size = 14),     
    legend.title = element_text(size = 14),
    panel.background = element_rect(fill = "white", color = NA),
    plot.background = element_rect(fill = "white", color = NA)
  )
    plot4 <- ggplot(get(paste0("temp_df_", element)), aes(x = row)) + 
  geom_line(aes(y = fw, color = "fw"), linewidth = 0.9) +
  geom_line(aes(y = vert, color = "vert"), linewidth = 0.9) +
  geom_line(aes(y = side, color = "side"), linewidth = 0.9) +
  labs(
    x = "Index",
    y = TeX(r'( Acceleration in $m/s^2$ )'),
    title = paste0("Temp: combined person ", element)) +
      scale_color_manual(
        name = "",
        values = c("fw" = "#56B4E9", "vert" = "#D62728", "side" = "#FFCC33")
        ) +
  theme_minimal() +
  theme(
    text = element_text(size = 14),      
    axis.title = element_text(size = 14),   
    axis.text = element_text(size = 14),      
    legend.text = element_text(size = 14),     
    legend.title = element_text(size = 14),
    panel.background = element_rect(fill = "white", color = NA),
    plot.background = element_rect(fill = "white", color = NA)
  )
  
  ggsave(paste0("avg_fw_", element,".png"), plot1, width = 10, height = 4, dpi = 600)
  ggsave(paste0("avg_vert_", element,".png"), plot2, width = 10, height = 4, dpi = 600)
  ggsave(paste0("avg_side_", element,".png"), plot3, width = 10, height = 4, dpi = 600)
  ggsave(paste0("avg_comb_", element,".png"), plot4, width = 10, height = 4, dpi = 600)
}
```

Looks weird. Lack of data?

```{r}
fw_vert_side_misc2_1[[4]] #216 steps
fw_vert_side_misc2_2[[4]] #404 steps
```

### Moving away from the mean

We will now continue with our analysis by considering things more complex than the mean. First check if they give the same result.

```{r}
element <- "A20"
all <- list()
for(item in get(paste0(element, "_list"))){
  all <- append(all, item)
}

df_test <- df_vert_from_mvm(all, 250, freq_selector, c(14,21))
colnames(df_test) <- as.character(1:250)

colMeans(df_test) %>% plot(type = 'l')
fw_vert_side_A20[[2]] %>% plot(type = 'l')
```

Now try to see if we can get nice plots from this dataframe (maybe do not want to store all dataframes, so define a dataframe and then overwrite it to make the next figures or something).

1. Ribbon with some sort of deviation

```{r}
summary_df <- data.frame(
  time = 1:250,
  mean = colMeans(df_test),
  sd = apply(df_test, 2, sd)
)
ggplot(summary_df, aes(x = time)) + 
  geom_line(aes(y = mean), color = "#D62728", linewidth = 0.9) +
  geom_ribbon(aes(ymin = mean - sd, ymax = mean + sd), fill = "#D62728", alpha = 0.2) +
  labs(
    x = "Index",
    y = TeX(r'( Acceleration in $m/s^2$ )'),
    title = paste0("Temp: fw person ", element)) +
  theme_minimal() +
  theme(
    text = element_text(size = 14),      
    axis.title = element_text(size = 14),   
    axis.text = element_text(size = 14),      
    legend.text = element_text(size = 14),     
    legend.title = element_text(size = 14),
    panel.background = element_rect(fill = "white", color = NA),
    plot.background = element_rect(fill = "white", color = NA)
  )
```

2. Quantiles (similar, but not with standard deviation but actual number of values... right?)

```{r}
summary_df <- data.frame(
  time = 1:250,
  mean = colMeans(df_test),
  quant20 = colQuantile(df_test, frac = 0.2),
  quant40 = colQuantile(df_test, frac = 0.4),
  quant50 = colQuantile(df_test, frac = 0.5),
  quant60 = colQuantile(df_test, frac = 0.6),
  quant80 = colQuantile(df_test, frac = 0.8)
)
```

3. Densities

```{r}
df_long <- transpose(df_test)  # Transpose so each row is a time step
colnames(df_long) <- as.character(1:ncol(df_long))
df_long$step <- 1:nrow(df_long)  # Add time variable
df_long <- pivot_longer(df_long, cols = -step, names_to = "time", values_to = "acceleration")
df_long$time <- as.numeric(df_long$time)

# 2D density plot (hexbin alternative)
ggplot(df_long, aes(x = time, y = acceleration)) +
  geom_bin2d(bins = 70) +
  scale_fill_continuous(type = "gradient") +
  theme_bw()


ggplot(df_long, aes(x=time, y=acceleration) ) +
  geom_density_2d()
```

4. All lines with low alpha

```{r}
df_test$id <- 1:(nrow(df_test))
df_test_melted = melt(df_test, id.vars = 'id')
df_means <- aggregate(value ~ variable, data = df_test_melted, FUN = mean)

df_test_melted$variable <- as.numeric(as.character(df_test_melted$variable))
df_means$variable <- as.numeric(as.character(df_means$variable))

ggplot(df_test_melted, aes(x = variable, y = value)) + 
  geom_line(aes(group = id), color = "#D62728", linewidth = 0.05, alpha = 0.02) +
  geom_line(data = df_means, aes(x = variable, y = value, group = 1), 
            color = "black", linewidth = 0.5) +
  labs(
    x = "Index",
    y = TeX(r'( Acceleration in $m/s^2$ )'),
    title = paste0("Temp: fw person ", element)) +
  ylim(-1, 0.9) +
  theme_minimal() +
  theme(
    text = element_text(size = 14),      
    axis.title = element_text(size = 14),   
    axis.text = element_text(size = 14),      
    legend.text = element_text(size = 14),     
    legend.title = element_text(size = 14),
    panel.background = element_rect(fill = "white", color = NA),
    plot.background = element_rect(fill = "white", color = NA)
  )
```

5. Figuring out why A20 (and A21) seem to contain two different movements

```{r}
which(df_test$`50` > 0.75)

data <- all
n <- 250
filter_function <- freq_selector
filter_par <- c(14,21)

  all_steps <- list()
  added_steps <- 0
  
  for(mvm in data){
    mvm_steps <- list()
    
    if(mvm$movement_type == "Walk" & filter_function(mvm, filter_par)){
      
      end_bw <- max(mvm$data$in_step_bw)
      end_fw <- max(mvm$data$in_step_fw)
      
      for(j in 1:end_bw){
        step <- filter(mvm$data, in_step_bw == j)
        new_vert <- rescale(step$acc_vert, n)
        
        mvm_steps <- append(mvm_steps, list(new_vert))
        added_steps <- added_steps + 1
        if(added_steps == 3326){
          print(mvm$data$time[1])
        }
        if(added_steps == 3361){
          print(mvm$data$time[1])
        }
      }
      
      for(j in 1:end_fw){
        step <- filter(mvm$data, in_step_fw == j)
        new_vert <- rescale(step$acc_vert, n)
        
        mvm_steps <- append(mvm_steps, list(new_vert))
        added_steps <- added_steps + 1
        
        if(added_steps == 3326){
          print(mvm$data$time[1])
        }
        if(added_steps == 3361){
          print(mvm$data$time[1])
        }
      }
      
      mvm_vert_avg <- numeric(n)
    }
    
    if(length(mvm_steps) > 0){
      for(j in 1:length(mvm_steps)){
        mvm_vert_avg <- mvm_vert_avg + mvm_steps[[j]]
      }
      min_index <- which.min(mvm_vert_avg)
      #Now we cycle every rescaled step in mvm_steps individually and add them to the df
      for(step in mvm_steps){
        if(min_index != 1){
          step <-  c(step[min_index:n], step[1:(min_index-1)])
          all_steps <- append(all_steps, list(step))
        }
      }
    }
  }
```

Testing down, we now make the figures that we are happy with for all:

```{r}
for(element in c("S1", "S2", "S3", "S4", "S5", "S6", "S7", "S8", "S9", 
                 "H10", "H11", "H12", "H13", "H14", "H15", "H16", "H17", "H18", "H19",
                 "A20", "A21")){
  all <- list()
  for(item in get(paste0(element, "_list"))){
    all <- append(all, item)
    }
  
  df_test <- df_vert_from_mvm(all, 250, filter_function, c(14,21))
  colnames(df_test) <- as.character(1:250)
  
df_test$id <- 1:(nrow(df_test))
df_test_melted = melt(df_test, id.vars = 'id')
df_means <- aggregate(value ~ variable, data = df_test_melted, FUN = mean)

df_test_melted$variable <- as.numeric(as.character(df_test_melted$variable))
df_means$variable <- as.numeric(as.character(df_means$variable))

plot <- ggplot(df_test_melted, aes(x = variable, y = value)) + 
  geom_line(aes(group = id), color = "#D62728", linewidth = 0.05, alpha = 200/nrow(df_test)) +
  geom_line(data = df_means, aes(x = variable, y = value, group = 1), 
            color = "black", linewidth = 0.5) +
  labs(
    x = "Index",
    y = TeX(r'( Acceleration in $m/s^2$ )'),
    title = paste0("Temp: vert person ", element)) +
  ylim(-1, 0.9) +
  theme_minimal() +
  theme(
    text = element_text(size = 14),      
    axis.title = element_text(size = 14),   
    axis.text = element_text(size = 14),      
    legend.text = element_text(size = 14),     
    legend.title = element_text(size = 14),
    panel.background = element_rect(fill = "white", color = NA),
    plot.background = element_rect(fill = "white", color = NA)
  )

  ggsave(paste0("distr_vert_", element,".png"), plot, width = 10, height = 4, dpi = 600)
}

df_silly1 <- df_vert_from_mvm(list(seq_silly[[1]], seq_silly[[2]], seq_silly[[3]], seq_silly[[4]]), 250, default, 0)
df_silly5 <- df_vert_from_mvm(list(seq_silly[[5]], seq_silly[[6]], seq_silly[[7]]), 250, default, 0)
df_silly6 <- df_vert_from_mvm(list(seq_silly[[8]], seq_silly[[9]]), 250, default, 0)
df_misc2_1 <- df_vert_from_mvm(seq_misc2_1, 250, freq_selector, c(14,21))
df_misc2_2 <- df_vert_from_mvm(seq_misc2_2, 250, freq_selector, c(14,21))

for(element in c("silly1", "silly5", "silly6", "misc2_1", "misc2_2")){
  
  df_test <- get(paste0("df_", element))
  colnames(df_test) <- as.character(1:250)
  
  df_test$id <- 1:(nrow(df_test))
df_test_melted = melt(df_test, id.vars = 'id')
df_means <- aggregate(value ~ variable, data = df_test_melted, FUN = mean)

df_test_melted$variable <- as.numeric(as.character(df_test_melted$variable))
df_means$variable <- as.numeric(as.character(df_means$variable))

plot <- ggplot(df_test_melted, aes(x = variable, y = value)) + 
  geom_line(aes(group = id), color = "#D62728", linewidth = 0.05, alpha = 200/nrow(df_test)) +
  geom_line(data = df_means, aes(x = variable, y = value, group = 1), 
            color = "black", linewidth = 0.5) +
  labs(
    x = "Index",
    y = TeX(r'( Acceleration in $m/s^2$ )'),
    title = paste0("Temp: vert person ", element)) +
  ylim(-1, 0.9) +
  theme_minimal() +
  theme(
    text = element_text(size = 14),      
    axis.title = element_text(size = 14),   
    axis.text = element_text(size = 14),      
    legend.text = element_text(size = 14),     
    legend.title = element_text(size = 14),
    panel.background = element_rect(fill = "white", color = NA),
    plot.background = element_rect(fill = "white", color = NA)
  )

  ggsave(paste0("distr_vert_", element,".png"), plot, width = 10, height = 4, dpi = 600)
}
```

```{r}
for(element in c("S1", "S2", "S3", "S4", "S5", "S6", "S7", "S8", "S9", 
                 "H10", "H11", "H12", "H13", "H14", "H15", "H16", "H17", "H18", "H19",
                 "A20", "A21")){
  all <- list()
  for(item in get(paste0(element, "_list"))){
    all <- append(all, item)
    }
  
  df_test <- df_fw_from_mvm(all, 250, filter_function, c(14,21))
  colnames(df_test) <- as.character(1:250)
  
df_test$id <- 1:(nrow(df_test))
df_test_melted = melt(df_test, id.vars = 'id')
df_means <- aggregate(value ~ variable, data = df_test_melted, FUN = mean)

df_test_melted$variable <- as.numeric(as.character(df_test_melted$variable))
df_means$variable <- as.numeric(as.character(df_means$variable))

plot <- ggplot(df_test_melted, aes(x = variable, y = value)) + 
  geom_line(aes(group = id), color = "#56B4E9", linewidth = 0.05, alpha = 300/nrow(df_test)) +
  geom_line(data = df_means, aes(x = variable, y = value, group = 1), 
            color = "black", linewidth = 0.5) +
  labs(
    x = "Index",
    y = TeX(r'( Acceleration in $m/s^2$ )'),
    title = paste0("Temp: fw person ", element)) +
  ylim(-0.5, 0.5) +
  theme_minimal() +
  theme(
    text = element_text(size = 14),      
    axis.title = element_text(size = 14),   
    axis.text = element_text(size = 14),      
    legend.text = element_text(size = 14),     
    legend.title = element_text(size = 14),
    panel.background = element_rect(fill = "white", color = NA),
    plot.background = element_rect(fill = "white", color = NA)
  )

  ggsave(paste0("distr_fw_", element,".png"), plot, width = 10, height = 4, dpi = 600)
}

df_silly1 <- df_fw_from_mvm(list(seq_silly[[1]], seq_silly[[2]], seq_silly[[3]], seq_silly[[4]]), 250, default, 0)
df_silly5 <- df_fw_from_mvm(list(seq_silly[[5]], seq_silly[[6]], seq_silly[[7]]), 250, default, 0)
df_silly6 <- df_fw_from_mvm(list(seq_silly[[8]], seq_silly[[9]]), 250, default, 0)
df_misc2_1 <- df_fw_from_mvm(seq_misc2_1, 250, freq_selector, c(14,21))
df_misc2_2 <- df_fw_from_mvm(seq_misc2_2, 250, freq_selector, c(14,21))

for(element in c("silly1", "silly5", "silly6", "misc2_1", "misc2_2")){
  
  df_test <- get(paste0("df_", element))
  colnames(df_test) <- as.character(1:250)
  
  df_test$id <- 1:(nrow(df_test))
df_test_melted = melt(df_test, id.vars = 'id')
df_means <- aggregate(value ~ variable, data = df_test_melted, FUN = mean)

df_test_melted$variable <- as.numeric(as.character(df_test_melted$variable))
df_means$variable <- as.numeric(as.character(df_means$variable))

plot <- ggplot(df_test_melted, aes(x = variable, y = value)) + 
  geom_line(aes(group = id), color = "#56B4E9", linewidth = 0.05, alpha = 300/nrow(df_test)) +
  geom_line(data = df_means, aes(x = variable, y = value, group = 1), 
            color = "black", linewidth = 0.5) +
  labs(
    x = "Index",
    y = TeX(r'( Acceleration in $m/s^2$ )'),
    title = paste0("Temp: fw person ", element)) +
  ylim(-0.5, 0.5) +
  theme_minimal() +
  theme(
    text = element_text(size = 14),      
    axis.title = element_text(size = 14),   
    axis.text = element_text(size = 14),      
    legend.text = element_text(size = 14),     
    legend.title = element_text(size = 14),
    panel.background = element_rect(fill = "white", color = NA),
    plot.background = element_rect(fill = "white", color = NA)
  )

  ggsave(paste0("distr_fw_", element,".png"), plot, width = 10, height = 4, dpi = 600)
}
```

```{r}
for(element in c("S1", "S2", "S3", "S4", "S5", "S6", "S7", "S8", "S9", 
                 "H10", "H11", "H12", "H13", "H14", "H15", "H16", "H17", "H18", "H19",
                 "A20", "A21")){
  all <- list()
  for(item in get(paste0(element, "_list"))){
    all <- append(all, item)
    }
  df_test <- df_side_from_mvm(all, 250, filter_function, c(14,21))
  colnames(df_test) <- as.character(1:250)
  
  df_test$id <- 1:(nrow(df_test))
df_test_melted = melt(df_test, id.vars = 'id')
df_means <- aggregate(value ~ variable, data = df_test_melted, FUN = mean)

df_test_melted$variable <- as.numeric(as.character(df_test_melted$variable))
df_means$variable <- as.numeric(as.character(df_means$variable))

plot <- ggplot(df_test_melted, aes(x = variable, y = value)) + 
  geom_line(aes(group = id), color = "#FFCC33", linewidth = 0.05, alpha = 300/nrow(df_test)) +
  geom_line(data = df_means, aes(x = variable, y = value, group = 1), 
            color = "black", linewidth = 0.5) +
  labs(
    x = "Index",
    y = TeX(r'( Acceleration in $m/s^2$ )'),
    title = paste0("Temp: side person ", element)) +
  ylim(-0.25, 0.25) +
  theme_minimal() +
  theme(
    text = element_text(size = 14),      
    axis.title = element_text(size = 14),   
    axis.text = element_text(size = 14),      
    legend.text = element_text(size = 14),     
    legend.title = element_text(size = 14),
    panel.background = element_rect(fill = "white", color = NA),
    plot.background = element_rect(fill = "white", color = NA)
  )

  ggsave(paste0("distr_side_", element,".png"), plot, width = 10, height = 4, dpi = 600)
}

df_silly1 <- df_side_from_mvm(list(seq_silly[[1]], seq_silly[[2]], seq_silly[[3]], seq_silly[[4]]), 250, default, 0)
df_silly5 <- df_side_from_mvm(list(seq_silly[[5]], seq_silly[[6]], seq_silly[[7]]), 250, default, 0)
df_silly6 <- df_side_from_mvm(list(seq_silly[[8]], seq_silly[[9]]), 250, default, 0)
df_misc2_1 <- df_side_from_mvm(seq_misc2_1, 250, freq_selector, c(14,21))
df_misc2_2 <- df_side_from_mvm(seq_misc2_2, 250, freq_selector, c(14,21))

for(element in c("silly1", "silly5", "silly6", "misc2_1", "misc2_2")){
  
  df_test <- get(paste0("df_", element))
  colnames(df_test) <- as.character(1:250)
  
  df_test$id <- 1:(nrow(df_test))
df_test_melted = melt(df_test, id.vars = 'id')
df_means <- aggregate(value ~ variable, data = df_test_melted, FUN = mean)

df_test_melted$variable <- as.numeric(as.character(df_test_melted$variable))
df_means$variable <- as.numeric(as.character(df_means$variable))

plot <- ggplot(df_test_melted, aes(x = variable, y = value)) + 
  geom_line(aes(group = id), color = "#FFCC33", linewidth = 0.05, alpha = 300/nrow(df_test)) +
  geom_line(data = df_means, aes(x = variable, y = value, group = 1), 
            color = "black", linewidth = 0.5) +
  labs(
    x = "Index",
    y = TeX(r'( Acceleration in $m/s^2$ )'),
    title = paste0("Temp: side person ", element)) +
  ylim(-0.3, 0.3) +
  theme_minimal() +
  theme(
    text = element_text(size = 14),      
    axis.title = element_text(size = 14),   
    axis.text = element_text(size = 14),      
    legend.text = element_text(size = 14),     
    legend.title = element_text(size = 14),
    panel.background = element_rect(fill = "white", color = NA),
    plot.background = element_rect(fill = "white", color = NA)
  )

  ggsave(paste0("distr_side_", element,".png"), plot, width = 10, height = 4, dpi = 600)
}
```
