### Importing libraries

```{r, message=F, warning=F}
library(tidyverse)
```

```{r}
df_part_trim <- df_part_trim %>% mutate(idx = 1:nrow(df_part_trim))
```

Pipeline is establishing start period roughly myself, then writing function to again take largest difference between moving average on left and moving average on right within that period (could maybe even use old function). Or just by hand, as there is not one perfect way to do it anyway. 

```{r}
#Filtering by time
start_time <- as.POSIXct("2024-10-10 14:26:00.000")
end_time <- as.POSIXct("2024-10-10 14:34:00.000")

df_part_trim %>% filter(time >= start_time & time <= end_time) %>% ggplot(aes(x = time)) + 
  geom_line(aes(y = Y)) + 
  geom_line(aes(y = ifelse(activity_partition == 0, 0, 0.5)), colour = "red") 

df_part_trim %>% filter(time >= start_time & time <= end_time) %>% pull(activity_partition) %>% min()
df_part_trim %>% filter(time >= start_time & time <= end_time) %>% pull(idx) %>% min()

#Filtering by partition element
part_element <- 54

df_part_trim %>% filter(activity_partition == part_element) %>% ggplot(aes(x = time)) + 
  geom_line(aes(y = vec_diff)) + 
  geom_line(aes(y = ifelse(activity_partition == 0, 0, 0.5)), colour = "red") 

df_part_trim %>% filter(activity_partition == part_element) %>% pull(time) %>% min()
df_part_trim %>% filter(activity_partition == part_element) %>% pull(time) %>% max()
df_part_trim %>% filter(activity_partition == part_element) %>% pull(idx) %>% min()
df_part_trim %>% filter(activity_partition == part_element) %>% pull(idx) %>% max()


#Filtering by index
start_idx <- 305000 
stop_idx <- 315000

df_part_trim %>% filter(idx >= start_idx & idx <= stop_idx) %>% ggplot(aes(x = time)) + 
  geom_line(aes(y = Z)) + 
  geom_line(aes(y = ifelse(activity_partition == 0, 0, 0.5)), colour = "red") 

df_part_trim %>% filter(idx >= start_idx & idx <= stop_idx) %>% pull(time) %>% min()
df_part_trim %>% filter(idx >= start_idx & idx <= stop_idx) %>% pull(time) %>% max()
df_part_trim %>% filter(idx >= start_idx & idx <= stop_idx) %>% pull(idx) %>% min()
```

```{r}
view(df_part_trim %>% filter(time >= start_time & time <= end_time))

view(df_part_trim[5644150:5695381,])
```

Storing running. _How to deal with fact that it is not a full active period? The activity detection becomes a bit obsolete if we do it by hand anyway. Or ma-left and ma-right for different statistics, and if difference still very big at some point then we have had some activity switch. For now just store the relevant indices_

```{r}
run_idx_1 <- c(5644150, 5695381) #Curated, part of partition element 354

#Combine
run_idx <- list(run_idx_1)

#run_idc[[1]][1]:run_idc[[1]][2]
```


Storing walking (walking definite, walking with possible noise, stops and short stairs such as to and from tram and train).

```{r}
walk_idx_1 <- c(894364, 909318) #Partition element 58
walk_idx_2 <- c(910255, 927158) #Partition element 59
walk_idx_3 <- c(252389, 271561) #Curated, part of partition element 30
walk_idx_4 <- c(387121, 407109) #Partition element 41, could be small pauses
walk_idx_5 <- c(11109981, 11112687) #Partition element 602
walk_idx_6 <- c(11112922, 11124060) #Partition element 603
walk_idx_7 <- c(11563331, 11578797) #Partition element 659
walk_idx_8 <- c(754311, 774526) #Partition element 54, but contains stairs at the end
walk_idx_9 <- c(751498, 753932)  #Partition element 53
walk_idx_10 <- c(910801, 925201) #Walk Apeldoorn roughly

#Combine
walk_idx <- list(walk_idx_1, walk_idx_2, walk_idx_3, walk_idx_4, walk_idx_5, walk_idx_6, walk_idx_7, walk_idx_8, walk_idx_9)
```

Storing stairs going up

```{r}
#All curated and part of partition element 30
#To be sure we only took stairs, we sometimes cut one possible part of the movement at the edges. We also did not include the platform in the middle
#Also: made sure to be full periods, so not from peak to valley. All in Z axis
stairs_up_idx_1 <- c(271601, 271803) 
stairs_up_idx_2 <- c(271881, 272058)
stairs_up_idx_3 <- c(272791, 273016)
stairs_up_idx_4 <- c(273095, 273308)
stairs_up_idx_5 <- c(273973, 274160)
stairs_up_idx_6 <- c(274251, 274524)
stairs_up_idx_7 <- c(275169, 275415)
stairs_up_idx_8 <- c(275524, 275721)

#Curated, part of partition element ...


#Combine
stairs_up_idx <- list(stairs_up_idx_1, stairs_up_idx_2, stairs_up_idx_3, stairs_up_idx_4, stairs_up_idx_5, stairs_up_idx_6, stairs_up_idx_7, stairs_up_idx_8)
```

Storing stairs going down

```{r}
#All curated and part of partition element 30
#To be sure we only took stairs, we sometimes cut one possible part of the movement at the edges. We also did not include the platform in the middle
#Also: made sure to be full periods, so not from peak to valley. All in Y axis
stairs_down_idx_1 <- c(272234, 272446)
stairs_down_idx_2 <- c(272503, 272724)
stairs_down_idx_3 <- c(273402, 273616)
stairs_down_idx_4 <- c(273696, 273883)
stairs_down_idx_5 <- c(274576, 274807)
stairs_down_idx_6 <- c(274904, 275095)
stairs_down_idx_7 <- c(275802, 276028)
stairs_down_idx_8 <- c(276129, 276317)

stairs_down_idx <- list(stairs_down_idx_1, stairs_down_idx_2, stairs_down_idx_3, stairs_down_idx_4, stairs_down_idx_5, stairs_down_idx_6, stairs_down_idx_7, stairs_down_idx_8)
```

Storing cycling

```{r}
#Most quite loosely curated to be sure I was on the bike
cycle_idx_1 <- c(210601, 216241) #Curated, part of partition element 28
cycle_idx_2 <- c(1019701, 1024201) #Curated, part of partition element 67
cycle_idx_3 <- c(2857801, 2862301) #Curated, part of partition element 127
cycle_idx_4 <- c(3556801, 3562201) #Curated, part of partition element 176
cycle_idx_5 <- c(5828701, 5898601) #Curated, part of partition element 389
cycle_idx_6 <- c(5900401, 5908501) #Curated, part of partition element 390
cycle_idx_7 <- c(6398240, 6406169) #Partition element 428. Contains getting on/stopping
cycle_idx_8 <- c(6406469, 6420091) #Partition element 429. Contains getting on/stopping
cycle_idx_9 <- c(6420435, 6429355) #Partition element 430. Contains getting on/stopping
cycle_idx_10 <- c(6436351, 6471301) #Curated, part of partition element 431

cycle_idx <- list(cycle_idx_1, cycle_idx_2, cycle_idx_3, cycle_idx_4, cycle_idx_5, cycle_idx_6, cycle_idx_7, cycle_idx_8, cycle_idx_9, cycle_idx_10)
```

```{r}
inactive_seated_idx_1 <- c(5976001, 6030001) #Chess match
inactive_seated_idx_2 <- c(6192001, 6246001) #Chess match
inactive_seated_idx_3 <- c(1467001, 1566001) #Studying at desk
inactive_seated_idx_4 <- c(2997001, 3303001) #Studying at desk behind reception
inactive_seated_idx_5 <- c(547201, 741601) #Lecture at VU
inactive_seated_idx_6 <- c(2880001, 2928601) #In train
inactive_seated_idx_7 <- c(3456001, 3483001) #In bus

inactive_seated_idx <- list(inactive_seated_idx_1, inactive_seated_idx_2, inactive_seated_idx_3, inactive_seated_idx_4, inactive_seated_idx_5, inactive_seated_idx_6, inactive_seated_idx_7)
```

```{r}
car_idx_1 <- c(3928501, 3956401)
car_idx_2 <- c(4172401, 4208401)

car_idx <- list(car_idx_1, car_idx_2)
```

```{r}
inactive_off_idx_1 <- c(1584001, 2808001)
inactive_off_idx_2 <- c(4374001, 5607001)
inactive_off_idx_3 <- c(6831001, 8118001)
inactive_off_idx_4 <- c(9099001, 10710001)
inactive_off_idx_5 <- c(12078001, 13284001)
inactive_off_idx_6 <- c(14661001, 15687001)

inactive_off_idx <- list(inactive_off_idx_1, inactive_off_idx_2, inactive_off_idx_3, inactive_off_idx_4, inactive_off_idx_5, inactive_off_idx_6)
```

```{r}
inactive_standing_idx_1 <- c(286201, 297001) #Train station
inactive_standing_idx_2 <- c(228601, 246601) #In train
inactive_standing_idx_3 <- c(11124151, 11125051) #Tram station
inactive_standing_idx_4 <- c(10748401, 10751701) #Train station

inactive_standing_idx <- list(inactive_standing_idx_1, inactive_standing_idx_2, inactive_standing_idx_3, inactive_standing_idx_4)
```

```{r}
#E.g. putting on, just making some random movements to see what happens, etc. "Random" or "noisy" in some sense, can be very different and different positions as well
noise_active_idx_1 <- c(83821, 84061) #Putting on accelerometer
noise_active_idx_2 <- c()  #Was wrong, removed
noise_active_idx_3 <- c() #Was wrong, removed

noise_active_idx <- list(noise_active_idx_1, noise_active_idx_2, noise_active_idx_3)
```

```{r}
#Activity done while standing, such as cooking, dishes etc., but without really walking
stand_active_idx_1 <- c(6420435, 6429355) #Doing dishes. Check!
stand_active_idx_2 <- c(144001, 153001) #Part morning routine
stand_active_idx_3 <- c(15825901, 15827701) #Somewhat active in gym, but no exercises. Maybe standing around, racking some weights
stand_active_idx_4 <- c()
stand_active_idx_5 <- c()

stand_active_idx <- list(stand_active_idx_1, stand_active_idx_2, stand_active_idx_3)
```

```{r}
misc_active_idx_1 <- c(15864601, 15865801) #Incline bench press

misc_active_idx <- list(misc_active_idx_1)
```

Later add e.g. pull-up, squat, calf raise, more types of walking and stairs. Also squatting/reaching/vacuuming, both dishwashing and shave+brush routine, jumping.
Movements still missing do on Wednesday. 

```{r}

```